```{r}
#| echo: false
#| output: false

source(here::here("src", "init.R"), echo = FALSE)

current_response <- insight::find_response(models[[1]]) # It should be the same for all compared models ...
current_predictor_set <- purrr::reduce(purrr::map(models, \(m) insight::find_predictors(m)$conditional), \(acc, l) union(acc, l))

pred2 <- NULL
if (length(current_predictor_set) >= 2) pred2 <- stringr::str_subset(current_predictor_set, "Condition", negate = TRUE)[[1]]

effects_template_path <- config$templates$effects
if (!exists("is_temporal")) is_temporal <- FALSE
if (is_temporal) effects_template_path <- config$templates$effects_temporal
```

### Data Exploration

```{r}
#| echo: false

dist_data <- distribution_summary(data, dvs = current_response, between = current_predictor_set) |> select(-Variable)

gt::gt(dist_data, auto_align = TRUE) |> 
  gt::fmt_number(columns = select(dist_data, where(\(v) is.numeric(v))) |> colnames(), decimals = 3, drop_trailing_zeros = TRUE)
```

```{r}
#| echo: false

hist_height <- 5

if(!is.null(pred2)) hist_height <- 4 + n_distinct(data[[pred2]])
```

```{r}
#| echo: false
#| fig.width: 8
#| fig.height: !expr hist_height

hist_plot(data, var = current_response, facet2 = pred2)
```

<!--[ Evolution ]-->

```{r}
#| eval: !expr is_temporal
#| echo: false
#| output: asis

cat("♦ Evolution:")
```

```{r}
#| eval: !expr is_temporal
#| echo: false
#| fig.width: 10
#| fig.height: 8

temporal_plot(data, resp = current_response, pred = "Condition", time = pred2)
```


<!------------------------------------------------------------------------------>
### Models & Diagnostics

```{r}
#| eval: !expr (!is_temporal)
#| echo: false
#| output: asis

cat("#### Welch t-test\n\n
:::{.callout-note}\n
Not used in the paper, shown for reference.\n\n
\n
We mimic a Welch t-test using a mixed-effects model and observation-level random effects.\n
:::\n
")
```

```{r}
#| eval: !expr (!is_temporal)
#| echo: !expr (!is_temporal)

mod_agg <- afex::mixed(
  paste0(current_response, " ~ Condition + (0 + dCondition | ID)"),
  data = data_agg,
  method = "S", # Satterthwaite df approximation
  control = lmerControl(
    check.nobs.vs.nlev = "ignore", 
    check.nobs.vs.nRE = "ignore"
  )
)
```

```{r}
#| eval: !expr (!is_temporal)
#| echo: false

parameters::parameters(
  mod_agg$full_model, effects = "fixed", 
  ci_method = "satterthwaite", drop = "Intercept"
) |> print_html()
```


#### Generalized Linear Mixed Models

Exploring candidate models:

::: {.panel-tabset}

```{r}
#| echo: false
#| results: asis

purrr::map(
  seq(1, length(models)),
  \(i) {
    mod <- models[[i]]
    knitr::knit_child(config$templates$mod, quiet = TRUE, envir = new.env(parent = environment()))
  }
) |> unlist() |> cat(sep = '\n')
```

:::

<!------------------------------------------------------------------------------>
### Effects Analysis

```{r}
#| echo: false

mod <- models[[1]] # First model of the list is the chosen one
```

:::{.callout-tip collapse="true"}

#### Chosen model: `r get_model_family(mod)`

```{r}
#| echo: false

print_model_call(mod)
```

:::

#### Coefficients

❖ All effects *(Wald)*:

```{r}
#| echo: false
#| output: false

all_effects <- parameters::parameters(
  mod, exponentiate = should_exp(mod), 
  p_adjust = "none", summary = TRUE, digits = 3
)
```

```{r}
#| eval: false

parameters::parameters(
  mod, exponentiate = should_exp(mod), 
  p_adjust = "none", summary = TRUE, digits = 3
)
```

```{r}
#| echo: false

print_html(all_effects)
```


❖ Main effects *(Wald Chi-Square)*:

```{r}
#| echo: false
#| output: false

anova_res <- car::Anova(mod, type = 3) |> broom::tidy() |> 
  filter(term != "(Intercept)") |> 
  mutate(p.value = label_pval(p.value)) |> 
  print_html()
```

```{r}
#| eval: false

car::Anova(mod, type = 3)
```

```{r}
#| echo: false

anova_res
```


❖ Main effects *(Likelihood Ratio Test)*:

```{r}
#| echo: false
#| output: false

lrt_res <- tryCatch(
  LRT(mod, pred = "Condition"),
  error = \(e) return(NULL)
)

display_lrt <- !is.null(lrt_res)
```

```{r}
#| eval: false
#| echo: !expr display_lrt

LRT(mod, pred = "Condition")
```

```{r}
#| eval: !expr (!display_lrt)
#| echo: false
#| output: asis

cat("*Likelihood Ratio is impossible to compute for this model ...*")
```

```{r}
#| eval: !expr display_lrt
#| echo: false

lrt_res |> as.data.frame() |> mutate(across(matches("^p.|^pr"), \(v) label_pval(v))) |> print_html()
```

::: {.column-margin}

:::{.callout-important}
Our `LRT()` method removes the predictor *plus* all its interactions
:::

:::

#### Marginal Effects

Marginal means & Contrasts of each predictor:

::: {.panel-tabset}

```{r}
#| echo: false
#| results: asis

preds <- c(insight::find_predictors(mod)$conditional, insight::find_interactions(mod)$conditional)

purrr::map(
  seq(1, length(preds)),
  \(i) {
    pred <- stringr::str_replace_all(preds[[i]], "[1-9]", "")
    knitr::knit_child(effects_template_path, quiet = TRUE, envir = new.env(parent = environment()))
  }
) |> unlist() |> cat(sep = '\n')
```

:::

```{r}
#| echo: false

is_temporal <- FALSE
```

***
