```{r include = F, echo = F}
source("../src/setup.R", echo = F)
```

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# I. Data:
***

```{r data}

BrDU_target <- "BrDU"

(BrDU_data <- load_BrDU(config$data$brDU_path) |> 
    group_by(Layer) |> 
    group_modify(\(d, g) mutate(d, !!paste0("Dens_BrDU_", g[["Layer"]][[1]]) := Dens_BrDU)) |> 
    ungroup()
)

### Variables:

BrDU_responses <- c("Dens_BrDU", "Dens_BrDU_EGL", "Dens_BrDU_IGL")
BrDU_predictors <- c("Layer", "Condition", "Mouse")

BrDU_data_EGL <- BrDU_data |> filter(Layer == "EGL") |> select(BrDU_predictors, matches("EGL"))
BrDU_data_IGL <- BrDU_data |> filter(Layer == "IGL") |> select(BrDU_predictors, matches("IGL"))

Dens_BrDU_name <- "Density of BrDU^(+) cells  \n *(10^(-5) cells/μm^(3))*"
Dens_BrDU_EGL_name <- "Density of BrDU^(+) cells in the EGL  \n *(10^(-5) cells/μm^(3))*"
Dens_BrDU_IGL_name <- "Density of BrDU^(+) cells in the IGL  \n *(10^(-5) cells/μm^(3))*"

contrasts(BrDU_data$Condition) <- contr.treatment

### Averaged data:

BrDU_data_agg <- BrDU_data |> 
  group_by(Layer, Mouse, Condition) |> 
  summarize(across(matches(BrDU_responses), .fns = \(.x) mean(.x, na.rm = T))) |> 
  ungroup() |> 
  mutate(dCondition = as.numeric(Condition == "IH")) |> 
  rowid_to_column("ID")
```

```{r}
BrDU_data %>% filter_all(any_vars(is.na(.)))
```

<!------------------------------------------------------------------------------>
## Correlations:
***

```{r fig.width = 8}
corr_matrix_plot(BrDU_data, vars = c(BrDU_responses, BrDU_predictors))
```

```{r fig.width = 8}
GGally::ggpairs(
  BrDU_data, columns = c(BrDU_responses, BrDU_predictors), 
  mapping = aes(color = Condition), lower = list(continuous = "smooth")
)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# II. Dens_BrDU_EGL:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distribution:

```{r}
distribution_summary(BrDU_data_EGL, dvs = "Dens_BrDU_EGL", between = "Condition")
```

```{r}
hist_plot(BrDU_data_EGL, var = "Dens_BrDU_EGL", facet = "Condition")
```


<!------------------------------------------------------------------------------>
## 2. Models:
***

<!------------------------------------------------------------------------------>
### Welch t-test:

On data aggregated by Mouse.
Data is assumed heteroscedastic in relation to `Condition`.

```{r}
BrDU_mod_Dens_BrDU_EGL_agg <- afex::mixed(
  Dens_BrDU_EGL ~ Condition + (0 + dCondition | ID),
  data = BrDU_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(BrDU_mod_Dens_BrDU_EGL_agg$full_model, effects = "fixed", ci_method = "wald", drop = "Intercept")
```

<!------------------------------------------------------------------------------>
### GLMM:

**Gaussian:**

```{r}
BrDU_mod_Dens_BrDU_EGL_gauss <- glmmTMB(
  Dens_BrDU_EGL ~ Condition + (1 | Mouse),
  data = BrDU_data_EGL,
  family = gaussian("log"),
  REML = T
)

parameters::parameters(BrDU_mod_Dens_BrDU_EGL_gauss)
cat("\n")
performance::performance(BrDU_mod_Dens_BrDU_EGL_gauss)
```

**Gamma:**

```{r}
BrDU_mod_Dens_BrDU_EGL_gamma <- glmmTMB(
  Dens_BrDU_EGL ~ Condition + (1 | Mouse),
  data = BrDU_data_EGL,
  family = Gamma("log"),
  REML = T
)

parameters::parameters(BrDU_mod_Dens_BrDU_EGL_gamma)
cat("\n")
performance::performance(BrDU_mod_Dens_BrDU_EGL_gamma)
```


<!------------------------------------------------------------------------------>
## 2. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(BrDU_mod_Dens_BrDU_EGL_gauss, BrDU_mod_Dens_BrDU_EGL_gamma)
```

Best model:

```{r}
BrDU_mod_Dens_BrDU_EGL <- BrDU_mod_Dens_BrDU_EGL_gamma
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 8}
make_acf_plot(BrDU_mod_Dens_BrDU_EGL)

performance::check_model(BrDU_mod_Dens_BrDU_EGL, detrend = TRUE)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

BrDU_mod_Dens_BrDU_EGL_dharma <- DHARMa::simulateResiduals(BrDU_mod_Dens_BrDU_EGL, plot = F, n = nsim, seed = getOption("seed"))
BrDU_mod_Dens_BrDU_EGL_dharma_t <- BrDU_mod_Dens_BrDU_EGL_dharma$simulatedResponse |> t()
```

```{r fig.width = 10}
ppc_plots(BrDU_mod_Dens_BrDU_EGL, simulations = BrDU_mod_Dens_BrDU_EGL_dharma_t, term = "Condition")
```

```{r fig.width = 10}
ppc_stat_plots(BrDU_mod_Dens_BrDU_EGL, simulations = BrDU_mod_Dens_BrDU_EGL_dharma_t, term = "Condition")
```

**Potential outliers:**

```{r}
insight::get_data(BrDU_mod_Dens_BrDU_EGL) |> 
  filter(!is.na(Dens_BrDU_EGL)) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(BrDU_mod_Dens_BrDU_EGL_dharma))
```


<!------------------------------------------------------------------------------>
## 3. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::parameters(
  BrDU_mod_Dens_BrDU_EGL, exponentiate = should_exp(BrDU_mod_Dens_BrDU_EGL), 
  ci_method = "wald", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(BrDU_mod_Dens_BrDU_EGL, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(BrDU_mod_Dens_BrDU_EGL, pred = "Condition")
```


<!------------------------------------------------------------------------------>
### Effects analysis:

**Condition:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(BrDU_mod_Dens_BrDU_EGL), dvs = insight::find_response(BrDU_mod_Dens_BrDU_EGL), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(BrDU_mod_Dens_BrDU_EGL, specs = "Condition", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(BrDU_mod_Dens_BrDU_EGL, specs = "Condition", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(BrDU_mod_Dens_BrDU_EGL, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 4.5, fig.height = 7}
make_signif_boxplot(BrDU_mod_Dens_BrDU_EGL, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(BrDU_mod_Dens_BrDU_EGL)}] Boxplots - by [Condition]"), subfolder = BrDU_target, dpi = dpi_save_png, width = 5, height = 8)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# III. Dens_BrDU_IGL:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distribution:

```{r}
distribution_summary(BrDU_data_IGL, dvs = "Dens_BrDU_IGL", between = "Condition")
```

```{r}
hist_plot(BrDU_data_IGL, var = "Dens_BrDU_IGL", facet = "Condition")
```


<!------------------------------------------------------------------------------>
## 2. Models:
***

<!------------------------------------------------------------------------------>
### Welch t-test:

On data aggregated by Mouse.
Data is assumed heteroscedastic in relation to `Condition`.

**With `t.test`:**

```{r}
BrDU_mod_Dens_BrDU_IGL_agg <- afex::mixed(
  Dens_BrDU_IGL ~ Condition + (0 + dCondition | ID),
  data = BrDU_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(BrDU_mod_Dens_BrDU_IGL_agg$full_model, effects = "fixed", ci_method = "wald", drop = "Intercept")
```

<!------------------------------------------------------------------------------>
### GLMM

**Gaussian:**

```{r}
BrDU_mod_Dens_BrDU_IGL_gauss <- glmmTMB(
  Dens_BrDU_IGL ~ Condition + (1 | Mouse),
  family = gaussian("log"),
  data = BrDU_data_IGL,
  REML = T
)

parameters::parameters(BrDU_mod_Dens_BrDU_IGL_gauss)
cat("\n")
performance::performance(BrDU_mod_Dens_BrDU_IGL_gauss)
```

**Gamma:**

```{r}
BrDU_mod_Dens_BrDU_IGL_gamma <- glmmTMB(
  Dens_BrDU_IGL ~ Condition + (1 | Mouse),
  family = Gamma("log"),
  data = BrDU_data_IGL,
  REML = T
)

parameters::parameters(BrDU_mod_Dens_BrDU_IGL_gamma)
cat("\n")
performance::performance(BrDU_mod_Dens_BrDU_IGL_gamma)
```

<!------------------------------------------------------------------------------>
## 2. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(BrDU_mod_Dens_BrDU_IGL_gauss, BrDU_mod_Dens_BrDU_IGL_gamma)
```

Best model:

```{r}
BrDU_mod_Dens_BrDU_IGL <- BrDU_mod_Dens_BrDU_IGL_gamma
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 8}
make_acf_plot(BrDU_mod_Dens_BrDU_IGL)

performance::check_model(BrDU_mod_Dens_BrDU_IGL, detrend = TRUE)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

BrDU_mod_Dens_BrDU_IGL_dharma <- DHARMa::simulateResiduals(BrDU_mod_Dens_BrDU_IGL, plot = F, n = nsim, seed = getOption("seed"))
BrDU_mod_Dens_BrDU_IGL_dharma_t <- BrDU_mod_Dens_BrDU_IGL_dharma$simulatedResponse |> t()
```

```{r fig.width = 10}
ppc_plots(BrDU_mod_Dens_BrDU_IGL, simulations = BrDU_mod_Dens_BrDU_IGL_dharma_t, term = "Condition")
```

```{r fig.width = 10}
ppc_stat_plots(BrDU_mod_Dens_BrDU_IGL, simulations = BrDU_mod_Dens_BrDU_IGL_dharma_t, term = "Condition")
```

**Potential outliers:**

```{r}
insight::get_data(BrDU_mod_Dens_BrDU_IGL) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(BrDU_mod_Dens_BrDU_IGL_dharma))
```


<!------------------------------------------------------------------------------>
## 3. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::parameters(
  BrDU_mod_Dens_BrDU_IGL, exponentiate = should_exp(BrDU_mod_Dens_BrDU_IGL), 
  ci_method = "Wald", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(BrDU_mod_Dens_BrDU_IGL, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(BrDU_mod_Dens_BrDU_IGL, pred = "Condition")
```


<!------------------------------------------------------------------------------>
### Marginal Effects:

**Condition:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(BrDU_mod_Dens_BrDU_IGL), dvs = insight::find_response(BrDU_mod_Dens_BrDU_IGL), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(BrDU_mod_Dens_BrDU_IGL, specs = "Condition", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(BrDU_mod_Dens_BrDU_IGL, specs = "Condition", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(BrDU_mod_Dens_BrDU_IGL, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 4.5, fig.height = 7}
make_signif_boxplot(BrDU_mod_Dens_BrDU_IGL, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(BrDU_mod_Dens_BrDU_IGL)}] Boxplots - by [Condition]"), subfolder = BrDU_target, dpi = dpi_save_png, width = 5, height = 8)
```



<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# IV. [Combined] GLMM:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distribution:

```{r}
distribution_summary(BrDU_data, dvs = "Dens_BrDU", between = c("Layer", "Condition"))
```

```{r}
hist_plot(BrDU_data, var = "Dens_BrDU", facet = "Condition") + facet_grid(vars(Layer), vars(Condition))
```


<!------------------------------------------------------------------------------>
## 2. Models:
***

**Gaussian:**

```{r}
BrDU_mod_Dens_BrDU_gauss <- glmmTMB(
  Dens_BrDU ~ Condition * Layer + (1 | Mouse),
  family = gaussian("log"),
  data = BrDU_data,
  REML = T
)

parameters(BrDU_mod_Dens_BrDU_gauss)
cat("\n")
performance(BrDU_mod_Dens_BrDU_gauss)
```

**Gamma:**

```{r}
BrDU_mod_Dens_BrDU_gamma <- glmmTMB(
  Dens_BrDU ~ Condition * Layer + (1 | Mouse),
  family = Gamma("log"),
  data = BrDU_data,
  REML = T
)

parameters(BrDU_mod_Dens_BrDU_gamma)
cat("\n")
performance(BrDU_mod_Dens_BrDU_gamma)
```


<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(BrDU_mod_Dens_BrDU_gauss, BrDU_mod_Dens_BrDU_gamma)
```

Best model:

```{r}
BrDU_mod_Dens_BrDU <- BrDU_mod_Dens_BrDU_gamma
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 8}
make_acf_plot(BrDU_mod_Dens_BrDU)

performance::check_model(BrDU_mod_Dens_BrDU, detrend = TRUE)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

BrDU_mod_Dens_BrDU_dharma <- DHARMa::simulateResiduals(BrDU_mod_Dens_BrDU, plot = F, n = nsim, seed = getOption("seed"))
BrDU_mod_Dens_BrDU_dharma_t <- BrDU_mod_Dens_BrDU_dharma$simulatedResponse |> t()
```

```{r fig.width = 10}
ppc_plots(BrDU_mod_Dens_BrDU, simulations = BrDU_mod_Dens_BrDU_dharma_t, term = "Condition")
ppc_plots(BrDU_mod_Dens_BrDU, simulations = BrDU_mod_Dens_BrDU_dharma_t, term = "Layer")
```

```{r fig.width = 10}
ppc_stat_plots(BrDU_mod_Dens_BrDU, simulations = BrDU_mod_Dens_BrDU_dharma_t, term = "Condition")
ppc_stat_plots(BrDU_mod_Dens_BrDU, simulations = BrDU_mod_Dens_BrDU_dharma_t, term = "Layer")
```

**Potential outliers:**

```{r fig.width = 10}
insight::get_data(BrDU_mod_Dens_BrDU) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(BrDU_mod_Dens_BrDU_dharma))
```


<!------------------------------------------------------------------------------>
## 4. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::parameters(
  BrDU_mod_Dens_BrDU, exponentiate = should_exp(BrDU_mod_Dens_BrDU), 
  ci_method = "Wald", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(BrDU_mod_Dens_BrDU, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(BrDU_mod_Dens_BrDU, pred = "Condition")
```


<!------------------------------------------------------------------------------>
### Marginal Effects:

**Condition**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(BrDU_mod_Dens_BrDU), dvs = insight::find_response(BrDU_mod_Dens_BrDU), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(BrDU_mod_Dens_BrDU, specs = "Condition", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(BrDU_mod_Dens_BrDU, specs = "Condition", type = "response") |>
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(BrDU_mod_Dens_BrDU, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 5, fig.height = 8}
# make_signif_boxplot(BrDU_mod_Dens_BrDU, xaxis = "Condition") |> 
#   save_png(filename = glue("[{get_model_tag(BrDU_mod_Dens_BrDU)}] Boxplots - by [Condition]"), subfolder = BrDU_target, dpi = dpi_save_png, width = 5, height = 8)
```

**Condition:Layer**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(BrDU_mod_Dens_BrDU), dvs = insight::find_response(BrDU_mod_Dens_BrDU), between = c("Layer", "Condition"))

log.main("===[Emmeans]===\n")

emmeans::emmeans(BrDU_mod_Dens_BrDU, specs = ~ Condition | Layer, type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(BrDU_mod_Dens_BrDU, specs = ~ Condition | Layer, type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(BrDU_mod_Dens_BrDU, specs = ~ Condition | Layer, type = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(BrDU_mod_Dens_BrDU, specs = ~ Condition | Layer, trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(BrDU_mod_Dens_BrDU, specs = ~ Condition | Layer, trans = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)
```

Plots:

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot(BrDU_mod_Dens_BrDU, xaxis = "Condition", facet = "Layer") |> 
  save_png(filename = glue("[{get_model_tag(BrDU_mod_Dens_BrDU)}] Boxplots - by [Condition] within [Layer]"), subfolder = BrDU_target, dpi = dpi_save_png, width = 6, height = 5)
```

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot_inter(BrDU_mod_Dens_BrDU, xaxis = "Condition", facet = "Layer") |> 
  save_png(filename = glue("[{get_model_tag(BrDU_mod_Dens_BrDU)}] Interaction Boxplots - by [Condition] within [Layer]"), subfolder = BrDU_target, dpi = dpi_save_png, width = 6, height = 5)
```