```{r include = F, echo = F}
source("../src/init.R", echo = F)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# I. Data:
***

```{r data}

Calb_P21_target <- "Calb-P21"

(Calb_P21_data <- load_Calb_P21(config$data$calb_P21_path))

### Variables:

Calb_P21_responses <- c("N_CC", "A_ML", "A_PC_per_cell", "Vol_PC_per_cell")
Calb_P21_predictors <- c("Condition", "Z", "Mouse")

N_CC_name <- "Number of Purkinje cell bodies  \n *(per 413x10^(3) µm^(3))*"
A_ML_name <- "Area of the ML *(10^(-4) µm^(2))*"
A_PC_per_cell_name <- "Purkinje dendrite area *(10^(-4) µm^(2))*  \n per Purkinje cell body"
Vol_PC_per_cell_name <- "Purkinje dendrite volume *(10^(-4) µm^(3))*  \n per Purkinje cell body"

contrasts(Calb_P21_data$Condition) <- contr.sum
contrasts(Calb_P21_data$Z) <- contr.sum

### Averaged data:

Calb_P21_data_agg <- Calb_P21_data |> 
  group_by(Mouse, Condition) |> 
  summarize(across(matches(Calb_P21_responses), .fns = \(.x) mean(.x, na.rm = T))) |> 
  ungroup() |> 
  mutate(dCondition = as.numeric(Condition == "IH")) |> 
  rowid_to_column("ID")
```

```{r}
Calb_P21_data %>% filter_all(any_vars(is.na(.)))
```

<!------------------------------------------------------------------------------>
## Correlations:
***

```{r fig.width = 8}
corr_matrix_plot(Calb_P21_data, vars = c(Calb_P21_predictors, Calb_P21_responses))
```

```{r fig.width = 12}
GGally::ggpairs(
  Calb_P21_data, columns = c(Calb_P21_predictors, Calb_P21_responses), 
  mapping = aes(color = Condition), lower = list(continuous = "smooth")
)
```

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# II. N_CC:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distributions:

**By Condition:**

```{r}
distribution_summary(Calb_P21_data, dvs = "N_CC", between = "Condition")
```

```{r}
hist_plot(Calb_P21_data, var = "N_CC", facet = "Condition")
```

**By Z:**

```{r}
distribution_summary(Calb_P21_data, dvs = "N_CC", between = "Z")
```

```{r}
hist_plot(Calb_P21_data, var = "N_CC", facet = "Z")
```

**By Condition:Z:**

```{r}
distribution_summary(Calb_P21_data, dvs = "N_CC", between = c("Condition", "Z"))
```

```{r}
hist_plot(Calb_P21_data, var = "N_CC") + facet_grid(rows = vars(Z), cols = vars(Condition))
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
## 2. Models:
***

<!------------------------------------------------------------------------------>
### Welch t-test:

On data averaged by Mouse.
Data is assumed heteroscedastic in relation to `Condition`.

```{r}
Calb_P21_mod_N_CC_agg <- afex::mixed(
  N_CC ~ Condition + (0 + dCondition | ID),
  data = Calb_P21_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(Calb_P21_mod_N_CC_agg$full_model, effects = "fixed", ci_method = "satterthwaite", drop = "Intercept")
```


<!------------------------------------------------------------------------------>
### GLMM:

**Poisson:**

```{r}
Calb_P21_mod_N_CC_poiss <- glmmTMB::glmmTMB(
  N_CC ~ Condition * Z + (1 | Mouse),
  family = poisson("log"),
  data = Calb_P21_data,
  REML = T,
  control = glmmTMBControl(optimizer = optim, optArgs = list(method = "BFGS"))
)

parameters(Calb_P21_mod_N_CC_poiss)
cat("\n")
performance(Calb_P21_mod_N_CC_poiss)
cat("\n")
check_overdispersion(Calb_P21_mod_N_CC_poiss)
```

**Negative binomial:**

```{r}
Calb_P21_mod_N_CC_nb <- glmmTMB::glmmTMB(
  N_CC ~ Condition * Z + (1 | Mouse),
  family = nbinom1("log"),
  data = Calb_P21_data,
  REML = T,
  control = glmmTMBControl(optimizer = optim, optArgs = list(method = "BFGS"))
)

parameters(Calb_P21_mod_N_CC_nb)
cat("\n")
performance(Calb_P21_mod_N_CC_nb)
cat("\n")
check_overdispersion(Calb_P21_mod_N_CC_nb)
```

**Generalized poisson:**

```{r}
Calb_P21_mod_N_CC_gp <- glmmTMB::glmmTMB(
  N_CC ~ Condition * Z + (1 | Mouse),
  family = genpois("log"),
  data = Calb_P21_data,
  REML = T
)

parameters(Calb_P21_mod_N_CC_gp)
cat("\n")
performance(Calb_P21_mod_N_CC_gp)
cat("\n")
check_overdispersion(Calb_P21_mod_N_CC_gp)
```

**COM Poisson:**

```{r}
Calb_P21_mod_N_CC_cmp <- glmmTMB::glmmTMB(
  N_CC ~ Condition * Z + (1 | Mouse),
  family = compois("log"),
  data = Calb_P21_data,
  REML = T
)

parameters(Calb_P21_mod_N_CC_cmp)
cat("\n")
performance(Calb_P21_mod_N_CC_cmp)
```


<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(Calb_P21_mod_N_CC_nb, Calb_P21_mod_N_CC_poiss, Calb_P21_mod_N_CC_gp, Calb_P21_mod_N_CC_cmp)
```

Best model:

```{r}
Calb_P21_mod_N_CC <- Calb_P21_mod_N_CC_gp
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 8}
performance::check_model(Calb_P21_mod_N_CC, detrend = TRUE)

make_acf_plot(Calb_P21_mod_N_CC)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

Calb_P21_mod_N_CC_dharma <- DHARMa::simulateResiduals(Calb_P21_mod_N_CC, plot = F, n = nsim, seed = getOption("seed"))
Calb_P21_mod_N_CC_dharma_t <- Calb_P21_mod_N_CC_dharma$simulatedResponse |> t()

plot(Calb_P21_mod_N_CC_dharma, quantreg = TRUE)
```

```{r fig.width = 10}
ppc_plots(Calb_P21_mod_N_CC, simulations = Calb_P21_mod_N_CC_dharma_t, term = "Condition")
ppc_plots(Calb_P21_mod_N_CC, simulations = Calb_P21_mod_N_CC_dharma_t, term = "Z")
```

```{r fig.width = 10}
ppc_stat_plots(Calb_P21_mod_N_CC, simulations = Calb_P21_mod_N_CC_dharma_t, term = "Condition")
ppc_stat_plots(Calb_P21_mod_N_CC, simulations = Calb_P21_mod_N_CC_dharma_t, term = "Z")
```

**Potential outliers:**

```{r fig.width = 10}
insight::get_data(Calb_P21_mod_N_CC) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(Calb_P21_mod_N_CC_dharma))
```


<!------------------------------------------------------------------------------>
## 4. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::parameters(
  Calb_P21_mod_N_CC, exponentiate = should_exp(Calb_P21_mod_N_CC), 
  ci_method = "Wald", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(Calb_P21_mod_N_CC, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(Calb_P21_mod_N_CC, pred = "Condition")
```


<!------------------------------------------------------------------------------>
### Marginal Effects:

**Condition:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(Calb_P21_mod_N_CC), dvs = insight::find_response(Calb_P21_mod_N_CC), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(Calb_P21_mod_N_CC, specs = "Condition", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(Calb_P21_mod_N_CC, specs = "Condition", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(Calb_P21_mod_N_CC, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 4, fig.height = 7}
make_signif_boxplot(Calb_P21_mod_N_CC, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(Calb_P21_mod_N_CC)}] Boxplots - by [Condition]"), subfolder = Calb_P21_target, dpi = 600, width = 5, height = 8)
```

**Z:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(Calb_P21_mod_N_CC), dvs = insight::find_response(Calb_P21_mod_N_CC), between = "Z")

log.main("===[Emmeans]===\n")

emmeans::emmeans(Calb_P21_mod_N_CC, specs = "Z", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(Calb_P21_mod_N_CC, specs = "Z", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(Calb_P21_mod_N_CC, specs = "Z", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 2, fig.height = 5}
make_signif_boxplot(Calb_P21_mod_N_CC, xaxis = "Z") |> 
  save_png(filename = glue("[{get_model_tag(Calb_P21_mod_N_CC)}] Boxplots - by [Z]"), subfolder = Calb_P21_target, dpi = 600, width = 4.5, height = 7)
```

**Condition:Z**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(Calb_P21_mod_N_CC), dvs = insight::find_response(Calb_P21_mod_N_CC), between = c("Condition", "Z"))

log.main("===[Emmeans]===\n")

emmeans::emmeans(Calb_P21_mod_N_CC, specs = ~ Z | Condition, type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(Calb_P21_mod_N_CC, specs = ~ Condition | Z, type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(Calb_P21_mod_N_CC, specs = ~ Condition | Z, type = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(Calb_P21_mod_N_CC, specs = ~ Condition | Z, trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(Calb_P21_mod_N_CC, specs = ~ Condition | Z, trans = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)
```

Plots:

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot(Calb_P21_mod_N_CC, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(Calb_P21_mod_N_CC)}] Boxplots - by [Condition] within [Z]"), subfolder = Calb_P21_target, dpi = 600, width = 10, height = 8)
```

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot_inter(Calb_P21_mod_N_CC, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(Calb_P21_mod_N_CC)}] Interaction Boxplots - by [Condition] within [Z]"), subfolder = Calb_P21_target, dpi = 600, width = 10, height = 8)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# III. A_ML:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distributions:

**By Condition:**

```{r}
distribution_summary(Calb_P21_data, dvs = "A_ML", between = "Condition")
```

```{r}
hist_plot(Calb_P21_data, var = "A_ML", facet = "Condition")
```

**By Z:**

```{r}
distribution_summary(Calb_P21_data, dvs = "A_ML", between = "Z")
```

```{r}
hist_plot(Calb_P21_data, var = "A_ML", facet = "Z")
```

**By Condition:Z:**

```{r}
distribution_summary(Calb_P21_data, dvs = "A_ML", between = c("Condition", "Z"))
```

```{r}
hist_plot(Calb_P21_data, var = "A_ML") + facet_grid(rows = vars(Z), cols = vars(Condition))
```


<!------------------------------------------------------------------------------>
## 2. Models:
***

<!------------------------------------------------------------------------------>
### Welch t-test:

On data averaged by Mouse.
Data is assumed heteroscedastic in relation to `Condition`.

```{r}
Calb_P21_mod_A_ML_agg <- afex::mixed(
  A_ML ~ Condition + (0 + dCondition | ID),
  data = Calb_P21_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(Calb_P21_mod_A_ML_agg$full_model, effects = "fixed", ci_method = "satterthwaite", drop = "Intercept")
```


<!------------------------------------------------------------------------------>
### GLMM:

**Gaussian:**

```{r}
Calb_P21_mod_A_ML_gauss <- glmmTMB(
  A_ML ~ Condition * Z + (1 | Mouse),
  family = gaussian("log"),
  data = Calb_P21_data,
  REML = T
)

parameters(Calb_P21_mod_A_ML_gauss)
cat("\n")
performance(Calb_P21_mod_A_ML_gauss)
```

**Gamma:**

```{r}
Calb_P21_mod_A_ML_gamma <- glmmTMB(
  A_ML ~ Condition * Z + (1 | Mouse),
  family = Gamma("log"),
  data = Calb_P21_data,
  REML = T,
  control = glmmTMBControl(optimizer = optim, optArgs = list(method = "BFGS"))
)

parameters(Calb_P21_mod_A_ML_gamma)
cat("\n")
performance(Calb_P21_mod_A_ML_gamma)
```

<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(Calb_P21_mod_A_ML_gauss, Calb_P21_mod_A_ML_gamma)
```

Best model:

```{r}
Calb_P21_mod_A_ML <- Calb_P21_mod_A_ML_gamma
```

<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 8}
performance::check_model(Calb_P21_mod_A_ML, detrend = TRUE)

make_acf_plot(Calb_P21_mod_A_ML)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

Calb_P21_mod_A_ML_dharma <- DHARMa::simulateResiduals(Calb_P21_mod_A_ML, plot = F, n = nsim, seed = getOption("seed"))
Calb_P21_mod_A_ML_dharma_t <- Calb_P21_mod_A_ML_dharma$simulatedResponse |> t()
```

```{r fig.width = 10}
ppc_plots(Calb_P21_mod_A_ML, simulations = Calb_P21_mod_A_ML_dharma_t, term = "Condition")
ppc_plots(Calb_P21_mod_A_ML, simulations = Calb_P21_mod_A_ML_dharma_t, term = "Z")
```

```{r fig.width = 10}
ppc_stat_plots(Calb_P21_mod_A_ML, simulations = Calb_P21_mod_A_ML_dharma_t, term = "Condition")
ppc_stat_plots(Calb_P21_mod_A_ML, simulations = Calb_P21_mod_A_ML_dharma_t, term = "Z")
```

**Potential outliers:**

```{r fig.width = 10}
insight::get_data(Calb_P21_mod_A_ML) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(Calb_P21_mod_A_ML_dharma))
```


<!------------------------------------------------------------------------------>
## 4. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::parameters(
  Calb_P21_mod_A_ML, exponentiate = should_exp(Calb_P21_mod_A_ML), 
  ci_method = "Wald", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(Calb_P21_mod_A_ML, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(Calb_P21_mod_A_ML, pred = "Condition")
```


<!------------------------------------------------------------------------------>
### Marginal Effects:

**Condition:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(Calb_P21_mod_A_ML), dvs = insight::find_response(Calb_P21_mod_A_ML), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(Calb_P21_mod_A_ML, specs = "Condition", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(Calb_P21_mod_A_ML, specs = "Condition", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(Calb_P21_mod_A_ML, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 4, fig.height = 7}
make_signif_boxplot(Calb_P21_mod_A_ML, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(Calb_P21_mod_A_ML)}] Boxplots - by [Condition]"), subfolder = Calb_P21_target, dpi = 600, width = 5, height = 8)
```

**Z:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(Calb_P21_mod_A_ML), dvs = insight::find_response(Calb_P21_mod_A_ML), between = "Z")

log.main("===[Emmeans]===\n")

emmeans::emmeans(Calb_P21_mod_A_ML, specs = "Z", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(Calb_P21_mod_A_ML, specs = "Z", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(Calb_P21_mod_A_ML, specs = "Z", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 2, fig.height = 5}
make_signif_boxplot(Calb_P21_mod_A_ML, xaxis = "Z") |> 
  save_png(filename = glue("[{get_model_tag(Calb_P21_mod_A_ML)}] Boxplots - by [Z]"), subfolder = Calb_P21_target, dpi = 600, width = 4.5, height = 7)
```

**Condition:Z**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(Calb_P21_mod_A_ML), dvs = insight::find_response(Calb_P21_mod_A_ML), between = c("Condition", "Z"))

log.main("===[Emmeans]===\n")

emmeans::emmeans(Calb_P21_mod_A_ML, specs = ~ Z | Condition, type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(Calb_P21_mod_A_ML, specs = ~ Condition | Z, type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(Calb_P21_mod_A_ML, specs = ~ Condition | Z, type = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(Calb_P21_mod_A_ML, specs = ~ Condition | Z, trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(Calb_P21_mod_A_ML, specs = ~ Condition | Z, trans = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)
```

Plots:

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot(Calb_P21_mod_A_ML, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(Calb_P21_mod_A_ML)}] Boxplots - by [Condition] within [Z]"), subfolder = Calb_P21_target, dpi = 600, width = 10, height = 8)
```

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot_inter(Calb_P21_mod_A_ML, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(Calb_P21_mod_A_ML)}] Interaction Boxplots - by [Condition] within [Z]"), subfolder = Calb_P21_target, dpi = 600, width = 10, height = 8)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# IV. A_PC_per_cell:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distributions:

**By Condition:**

```{r}
distribution_summary(Calb_P21_data, dvs = "A_PC_per_cell", between = "Condition")
```

```{r}
hist_plot(Calb_P21_data, var = "A_PC_per_cell", facet = "Condition")
```

**By Z:**

```{r}
distribution_summary(Calb_P21_data, dvs = "A_PC_per_cell", between = "Z")
```

```{r}
hist_plot(Calb_P21_data, var = "A_PC_per_cell", facet = "Z")
```

**By Condition:Z:**

```{r}
distribution_summary(Calb_P21_data, dvs = "A_PC_per_cell", between = c("Condition", "Z"))
```

```{r}
hist_plot(Calb_P21_data, var = "A_PC_per_cell") + facet_grid(rows = vars(Z), cols = vars(Condition))
```


<!------------------------------------------------------------------------------>
### Relationships:

```{r}
ggplot(Calb_P21_data, aes(x = A_ML, y = A_PC_per_cell, color = Condition, shape = Mouse)) + geom_point() + geom_smooth(method = "lm", se = F)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
## 2. Models:
***

<!------------------------------------------------------------------------------>
### Welch t-test:

On data averaged by Mouse.
Data is assumed heteroscedastic in relation to `Condition`.

```{r}
Calb_P21_mod_A_PC_agg <- afex::mixed(
  A_PC_per_cell ~ Condition + (0 + dCondition | ID),
  data = Calb_P21_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(Calb_P21_mod_A_PC_agg$full_model, effects = "fixed", ci_method = "satterthwaite", drop = "Intercept")
```


<!------------------------------------------------------------------------------>
### GLMM:

**Gaussian:**

```{r}
Calb_P21_mod_A_PC_gauss <- glmmTMB(
  A_PC_per_cell ~ Condition * Z + (1 | Mouse),
  family = gaussian("log"),
  data = Calb_P21_data,
  REML = T,
  control = glmmTMBControl(optimizer = optim, optArgs = list(method = "BFGS"))
)

parameters(Calb_P21_mod_A_PC_gauss)
cat("\n")
performance(Calb_P21_mod_A_PC_gauss)
```

**Gamma:**

```{r}
Calb_P21_mod_A_PC_gamma <- glmmTMB(
  A_PC_per_cell ~ Condition * Z + (1 | Mouse),
  family = Gamma("log"),
  data = Calb_P21_data,
  REML = T,
  control = glmmTMBControl(optimizer = optim, optArgs = list(method = "BFGS"))
)

parameters(Calb_P21_mod_A_PC_gamma)
cat("\n")
performance(Calb_P21_mod_A_PC_gamma)
```

**Gamma + offset for A_ML:**

```{r}
Calb_P21_mod_A_PC_gamma_off <- glmmTMB(
  A_PC_per_cell ~ Condition * Z + offset(log(A_ML)) + (1 | Mouse),
  family = Gamma("log"),
  data = Calb_P21_data,
  REML = T,
  control = glmmTMBControl(optimizer = optim, optArgs = list(method = "BFGS"))
)

parameters(Calb_P21_mod_A_PC_gamma_off)
cat("\n")
performance(Calb_P21_mod_A_PC_gamma_off)
```

<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(Calb_P21_mod_A_PC_gauss, Calb_P21_mod_A_PC_gamma)
```

Best model:

```{r}
Calb_P21_mod_A_PC <- Calb_P21_mod_A_PC_gamma
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 8}
performance::check_model(Calb_P21_mod_A_PC, detrend = TRUE)

make_acf_plot(Calb_P21_mod_A_PC)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

Calb_P21_mod_A_PC_dharma <- DHARMa::simulateResiduals(Calb_P21_mod_A_PC, plot = F, n = nsim, seed = getOption("seed"))
Calb_P21_mod_A_PC_dharma_t <- Calb_P21_mod_A_PC_dharma$simulatedResponse |> t()
```

```{r fig.width = 10}
ppc_plots(Calb_P21_mod_A_PC, simulations = Calb_P21_mod_A_PC_dharma_t, term = "Condition")
ppc_plots(Calb_P21_mod_A_PC, simulations = Calb_P21_mod_A_PC_dharma_t, term = "Z")
```

```{r fig.width = 10}
ppc_stat_plots(Calb_P21_mod_A_PC, simulations = Calb_P21_mod_A_PC_dharma_t, term = "Condition")
ppc_stat_plots(Calb_P21_mod_A_PC, simulations = Calb_P21_mod_A_PC_dharma_t, term = "Z")
```

**Potential outliers:**

```{r fig.width = 10}
insight::get_data(Calb_P21_mod_A_PC) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(Calb_P21_mod_A_PC_dharma))
```


<!------------------------------------------------------------------------------>
## 4. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::parameters(
  Calb_P21_mod_A_PC, exponentiate = should_exp(Calb_P21_mod_A_PC), 
  ci_method = "Wald", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(Calb_P21_mod_A_PC, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(Calb_P21_mod_A_PC, pred = "Condition")
```


<!------------------------------------------------------------------------------>
### Marginal Effects:

**Condition:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(Calb_P21_mod_A_PC), dvs = insight::find_response(Calb_P21_mod_A_PC), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(Calb_P21_mod_A_PC, specs = "Condition", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(Calb_P21_mod_A_PC, specs = "Condition", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(Calb_P21_mod_A_PC, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 4, fig.height = 7}
make_signif_boxplot(Calb_P21_mod_A_PC, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(Calb_P21_mod_A_PC)}] Boxplots - by [Condition]"), subfolder = Calb_P21_target, dpi = 600, width = 5, height = 8)
```

**Z:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(Calb_P21_mod_A_PC), dvs = insight::find_response(Calb_P21_mod_A_PC), between = "Z")

log.main("===[Emmeans]===\n")

emmeans::emmeans(Calb_P21_mod_A_PC, specs = "Z", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(Calb_P21_mod_A_PC, specs = "Z", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(Calb_P21_mod_A_PC, specs = "Z", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 4, fig.height = 7}
make_signif_boxplot(Calb_P21_mod_A_PC, xaxis = "Z") |> 
  save_png(filename = glue("[{get_model_tag(Calb_P21_mod_A_PC)}] Boxplots - by [Z]"), subfolder = Calb_P21_target, dpi = 600, width = 4.5, height = 7)
```

**Condition:Z**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(Calb_P21_mod_A_PC), dvs = insight::find_response(Calb_P21_mod_A_PC), between = c("Condition", "Z"))

log.main("===[Emmeans]===\n")

emmeans::emmeans(Calb_P21_mod_A_PC, specs = ~ Z | Condition, type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(Calb_P21_mod_A_PC, specs = ~ Condition | Z, type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(Calb_P21_mod_A_PC, specs = ~ Condition | Z, type = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(Calb_P21_mod_A_PC, specs = ~ Condition | Z, trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(Calb_P21_mod_A_PC, specs = ~ Condition | Z, trans = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)
```

Plots:

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot(Calb_P21_mod_A_PC, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(Calb_P21_mod_A_PC)}] Boxplots - by [Condition] within [Z]"), subfolder = Calb_P21_target, dpi = 600, width = 10, height = 8)
```

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot_inter(Calb_P21_mod_A_PC, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(Calb_P21_mod_A_PC)}] Interaction Boxplots - by [Condition] within [Z]"), subfolder = Calb_P21_target, dpi = 600, width = 10, height = 8)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# V. Vol_PC_per_cell:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distributions:

**By Condition:**

```{r}
distribution_summary(Calb_P21_data, dvs = "Vol_PC_per_cell", between = "Condition")
```

```{r}
hist_plot(Calb_P21_data, var = "Vol_PC_per_cell", facet = "Condition")
```

**By Z:**

```{r}
distribution_summary(Calb_P21_data, dvs = "Vol_PC_per_cell", between = "Z")
```

```{r}
hist_plot(Calb_P21_data, var = "Vol_PC_per_cell", facet = "Z")
```

**By Condition:Z:**

```{r}
distribution_summary(Calb_P21_data, dvs = "Vol_PC_per_cell", between = c("Condition", "Z"))
```

```{r}
hist_plot(Calb_P21_data, var = "Vol_PC_per_cell") + facet_grid(rows = vars(Z), cols = vars(Condition))
```


<!------------------------------------------------------------------------------>
### Relationships:

```{r}
ggplot(Calb_P21_data, aes(x = A_ML, y = Vol_PC_per_cell, color = Condition, shape = Mouse)) + geom_point() + geom_smooth(method = "lm", se = F)
```


<!------------------------------------------------------------------------------>
## 2. Models:
***

<!------------------------------------------------------------------------------>
### Welch t-test:

On data averaged by Mouse.
Data is assumed heteroscedastic in relation to `Condition`.

```{r}
Calb_P21_mod_Vol_PC_agg <- afex::mixed(
  Vol_PC_per_cell  ~ Condition + (0 + dCondition | ID),
  data = Calb_P21_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(Calb_P21_mod_Vol_PC_agg$full_model, effects = "fixed", ci_method = "satterthwaite", drop = "Intercept")
```


<!------------------------------------------------------------------------------>
### GLMM:

**Gaussian:**

```{r}
Calb_P21_mod_Vol_PC_gauss <- glmmTMB(
  Vol_PC_per_cell ~ Condition * Z + (1 | Mouse),
  family = gaussian("log"),
  data = Calb_P21_data,
  REML = T
)

parameters(Calb_P21_mod_Vol_PC_gauss)
cat("\n")
performance(Calb_P21_mod_Vol_PC_gauss)
```

**Gamma:**

```{r}
Calb_P21_mod_Vol_PC_gamma <- glmmTMB(
  Vol_PC_per_cell ~ Condition * Z + (1 | Mouse),
  family = Gamma("log"),
  data = Calb_P21_data,
  REML = T
)

parameters(Calb_P21_mod_Vol_PC_gamma)
cat("\n")
performance(Calb_P21_mod_Vol_PC_gamma)
```

**Gamma + offset for A_ML:**

```{r}
Calb_P21_mod_Vol_PC_gamma_off <- glmmTMB(
  Vol_PC_per_cell ~ Condition * Z + offset(log(A_ML)) + (1 | Mouse),
  family = Gamma("log"),
  data = Calb_P21_data,
  REML = T,
  control = glmmTMBControl(optimizer = optim, optArgs = list(method = "BFGS"))
)

parameters(Calb_P21_mod_Vol_PC_gamma_off)
cat("\n")
performance(Calb_P21_mod_Vol_PC_gamma_off)
```

<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(Calb_P21_mod_Vol_PC_gauss, Calb_P21_mod_Vol_PC_gamma)
```

Best model:

```{r}
Calb_P21_mod_Vol_PC <- Calb_P21_mod_Vol_PC_gamma
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 8}
performance::check_model(Calb_P21_mod_Vol_PC, detrend = TRUE)

make_acf_plot(Calb_P21_mod_Vol_PC)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

Calb_P21_mod_Vol_PC_dharma <- DHARMa::simulateResiduals(Calb_P21_mod_Vol_PC, plot = F, n = nsim, seed = getOption("seed"))
Calb_P21_mod_Vol_PC_dharma_t <- Calb_P21_mod_Vol_PC_dharma$simulatedResponse |> t()
```

```{r fig.width = 10}
ppc_plots(Calb_P21_mod_Vol_PC, simulations = Calb_P21_mod_Vol_PC_dharma_t, term = "Condition")
ppc_plots(Calb_P21_mod_Vol_PC, simulations = Calb_P21_mod_Vol_PC_dharma_t, term = "Z")
```

```{r fig.width = 10}
ppc_stat_plots(Calb_P21_mod_Vol_PC, simulations = Calb_P21_mod_Vol_PC_dharma_t, term = "Condition")
ppc_stat_plots(Calb_P21_mod_Vol_PC, simulations = Calb_P21_mod_Vol_PC_dharma_t, term = "Z")
```

**Potential outliers:**

```{r fig.width = 10}
insight::get_data(Calb_P21_mod_Vol_PC) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(Calb_P21_mod_Vol_PC_dharma))
```


<!------------------------------------------------------------------------------>
## 4. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::parameters(
  Calb_P21_mod_Vol_PC, exponentiate = should_exp(Calb_P21_mod_Vol_PC), 
  ci_method = "Wald", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(Calb_P21_mod_Vol_PC, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(Calb_P21_mod_Vol_PC, pred = "Condition")
```


<!------------------------------------------------------------------------------>
### Marginal Effects:

**Condition:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(Calb_P21_mod_Vol_PC), dvs = insight::find_response(Calb_P21_mod_Vol_PC), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(Calb_P21_mod_Vol_PC, specs = "Condition", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(Calb_P21_mod_Vol_PC, specs = "Condition", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(Calb_P21_mod_Vol_PC, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 4, fig.height = 7}
make_signif_boxplot(Calb_P21_mod_Vol_PC, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(Calb_P21_mod_Vol_PC)}] Boxplots - by [Condition]"), subfolder = Calb_P21_target, dpi = 600, width = 5, height = 8)
```

**Z:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(Calb_P21_mod_Vol_PC), dvs = insight::find_response(Calb_P21_mod_Vol_PC), between = "Z")

log.main("===[Emmeans]===\n")

emmeans::emmeans(Calb_P21_mod_Vol_PC, specs = "Z", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(Calb_P21_mod_Vol_PC, specs = "Z", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(Calb_P21_mod_Vol_PC, specs = "Z", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 5, fig.height = 7}
make_signif_boxplot(Calb_P21_mod_Vol_PC, xaxis = "Z") |> 
  save_png(filename = glue("[{get_model_tag(Calb_P21_mod_Vol_PC)}] Boxplots - by [Z]"), subfolder = Calb_P21_target, dpi = 600, width = 4.5, height = 7)
```

**Condition:Z**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(Calb_P21_mod_Vol_PC), dvs = insight::find_response(Calb_P21_mod_Vol_PC), between = c("Condition", "Z"))

log.main("===[Emmeans]===\n")

emmeans::emmeans(Calb_P21_mod_Vol_PC, specs = ~ Z | Condition, type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(Calb_P21_mod_Vol_PC, specs = ~ Condition | Z, type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(Calb_P21_mod_Vol_PC, specs = ~ Condition | Z, type = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(Calb_P21_mod_Vol_PC, specs = ~ Condition | Z, trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(Calb_P21_mod_Vol_PC, specs = ~ Condition | Z, trans = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)
```

Plots:

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot(Calb_P21_mod_Vol_PC, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(Calb_P21_mod_Vol_PC)}] Boxplots - by [Condition] within [Z]"), subfolder = Calb_P21_target, dpi = 600, width = 10, height = 8)
```

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot_inter(Calb_P21_mod_Vol_PC, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(Calb_P21_mod_Vol_PC)}] Interaction Boxplots - by [Condition] within [Z]"), subfolder = Calb_P21_target, dpi = 600, width = 10, height = 8)
```
