```{r include = F, echo = F}
source("../src/setup.R", echo = F)
```

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# I. Data:
***

```{r data}

Casp_Act_target <- "Casp-Act"

(Casp_Act_data <- load_Casp_Act(config$data$casp_Act_path))

### Variables:

Casp_Act_responses <- c("Fluo_Norm")
Casp_Act_predictors <- c("Condition", "Experiment", "Mouse")

Fluo_Norm_name <- "Enzymatic Activity of Caspase 3/7  \n *(Normalized Fluorescence)*"

contrasts(Casp_Act_data$Condition) <- contr.sum
contrasts(Casp_Act_data$Experiment) <- contr.sum
```

```{r}
Casp_Act_data |> filter(if_any(everything(), \(c) is.na(c)))
```

<!------------------------------------------------------------------------------>
## Correlations:
***

```{r fig.width = 8}
corr_matrix_plot(Casp_Act_data, vars = c(Casp_Act_predictors, Casp_Act_responses))
```

```{r fig.width = 8}
GGally::ggpairs(
  Casp_Act_data, columns = c(c("Condition", "Experiment"), Casp_Act_responses), 
  mapping = aes(color = Condition), lower = list(continuous = "smooth")
)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# II. Fluo_Norm:
***

**Normalizing by Normoxia: Hypoxia - Normoxia (within each experiment)**

```{r}
(Casp_Act_norm_data <- Casp_Act_data 
 |> group_by(Experiment, Condition)
 |> mutate(Avg_N = ifelse(Condition == "N", mean(Fluo_Norm), NA))
 |> group_by(Experiment)
 |> fill(Avg_N, .direction = "down")
 |> mutate(Fluo_Norm = Fluo_Norm - Avg_N)
 |> select(-Avg_N)
 |> ungroup()
)
```

<!------------------------------------------------------------------------------>
## 1. Data Exploration:

```{r}
distribution_summary(Casp_Act_norm_data, dvs = Casp_Act_responses, between = c("Condition", "Experiment"))
```

```{r fig.width = 6}
hist_plot(Casp_Act_norm_data, var = "Fluo_Norm") + facet_grid(rows = vars(Condition), cols = vars(Experiment))
```


<!------------------------------------------------------------------------------>
## 2. Models:

### a. Welch t-test:

```{r}
(Casp_Act_norm_data_agg <- Casp_Act_norm_data |> 
  group_by(Mouse, Condition) |> 
  summarize(Fluo_Norm = mean(Fluo_Norm)) |> 
  ungroup() |> 
  mutate(dCondition = as.numeric(Condition == "IH")) |> 
  rowid_to_column("ID")
)
```

```{r}
Casp_Act_mod_norm_agg <- afex::mixed(
  Fluo_Norm ~ Condition + (0 + dCondition | ID),
  data = Casp_Act_norm_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(Casp_Act_mod_norm_agg$full_model, effects = "fixed", ci_method = "satterthwaite", drop = "Intercept")
```

Mann-Whitney:

```{r}
wilcox.test(formula = Fluo_Norm ~ Condition, data = Casp_Act_norm_data_agg, paired = FALSE)
```


### b. GLMM:

```{r}
Casp_Act_mod_norm <- glmmTMB(
  Fluo_Norm ~ Condition + (1 | Mouse),
  family = gaussian("identity"),
  data = Casp_Act_norm_data,
  REML = T
)

parameters::parameters(Casp_Act_mod_norm)
cat("\n")
performance::performance(Casp_Act_mod_norm)
```


<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:

### a. Residuals:

```{r fig.width = 8}
make_acf_plot(Casp_Act_mod_norm)

performance::check_model(Casp_Act_mod_norm, detrend = TRUE)
```


### b. Predictions:

```{r}
nsim <- 300

Casp_Act_mod_norm_dharma <- DHARMa::simulateResiduals(Casp_Act_mod_norm, plot = F, n = nsim, seed = getOption("seed"))
Casp_Act_mod_norm_dharma_t <- Casp_Act_mod_norm_dharma$simulatedResponse |> t()
```

```{r fig.width = 10}
ppc_plots(Casp_Act_mod_norm, Casp_Act_mod_norm_dharma_t, term = "Condition")
```

```{r fig.width = 10}
ppc_stat_plots(Casp_Act_mod_norm, Casp_Act_mod_norm_dharma_t, term = "Condition")
```

**Potential outliers:**

```{r}
insight::get_data(Casp_Act_mod_norm) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(Casp_Act_mod_norm_dharma))
```


<!------------------------------------------------------------------------------>
## 4. Effects Analysis:

### a. Coefficients:

**All effects (Wald):**

```{r}
parameters::parameters(
  Casp_Act_mod_norm, exponentiate = should_exp(Casp_Act_mod_norm), 
  ci_method = "Kenward", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(Casp_Act_mod_norm, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(Casp_Act_mod_norm, pred = "Condition")
```


### b. Marginal Effects:

**Condition:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(Casp_Act_mod_norm), dvs = insight::find_response(Casp_Act_mod_norm), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(Casp_Act_mod_norm, specs = "Condition", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(Casp_Act_mod_norm, specs = "Condition", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(Casp_Act_mod_norm, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 5, fig.height = 8}
make_signif_boxplot(Casp_Act_mod_norm, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(Casp_Act_mod_norm)}] - [Normalized] Boxplots - by [Condition]"), subfolder = Casp_Act_target, dpi = dpi_save_png, width = 5, height = 8)
```

