```{r include = F, echo = F}
source("../src/setup.R", echo = F)
```

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# I. Data:
***

```{r data}

DAPI_Density_P12_target <- "DAPI_Density_P12"

(DAPI_Density_P12_data <- load_dapi_density_P12())

### Variables:

DAPI_Density_P12_responses <- c("Nb_Area", "Nb_Vol", "Avg_Distance")
DAPI_Density_P12_predictors <- c("Condition", "Mouse", "Layer")

Nb_Area_name <- "Cell density *(10^(-3) cell number/μm^(2))*"
Nb_Vol_name <- "Cell density *(10^(-2) cell number/μm^(3))*"
Avg_Distance_name <- "Average distance between cells *(μm)*"

contrasts(DAPI_Density_P12_data$Condition) <- contr.sum
contrasts(DAPI_Density_P12_data$Mouse) <- contr.sum
contrasts(DAPI_Density_P12_data$Layer) <- contr.sum

### Averaged data:

DAPI_Density_P12_data_agg <- DAPI_Density_P12_data |> 
  group_by(Mouse, Condition) |> 
  summarize(across(matches(DAPI_Density_P12_responses), .fns = \(.x) mean(.x, na.rm = T))) |> 
  ungroup() |> 
  mutate(
    dCondition = as.numeric(Condition == "IH"),
    ID = row_number()
  )
```

```{r}
DAPI_Density_P12_data |> filter(if_any(everything(), \(c) is.na(c)))
```


<!------------------------------------------------------------------------------>
## Correlations:
***

```{r fig.width = 8}
corr_matrix_plot(DAPI_Density_P12_data, vars = c(DAPI_Density_P12_predictors, DAPI_Density_P12_responses))
```

```{r fig.width = 10}
GGally::ggpairs(
  DAPI_Density_P12_data, columns = c(DAPI_Density_P12_predictors, DAPI_Density_P12_responses), 
  mapping = aes(color = Condition), lower = list(continuous = "smooth")
)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# II. Nb_Area:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distributions:

**By Condition:**

```{r}
distribution_summary(DAPI_Density_P12_data, dvs = "Nb_Area", between = "Condition")
```

```{r}
hist_plot(DAPI_Density_P12_data, var = "Nb_Area", facet = "Condition")
```

**By Layer:**

```{r}
distribution_summary(DAPI_Density_P12_data, dvs = "Nb_Area", between = "Layer")
```

```{r}
hist_plot(DAPI_Density_P12_data, var = "Nb_Area", facet = "Layer")
```

**By Condition:Layer:**

```{r}
distribution_summary(DAPI_Density_P12_data, dvs = "Nb_Area", between = c("Condition", "Layer"))
```

```{r}
hist_plot(DAPI_Density_P12_data, var = "Nb_Area") + facet_grid(rows = vars(Layer), cols = vars(Condition))
```


<!------------------------------------------------------------------------------>
## 2. Models:
***

<!------------------------------------------------------------------------------>
### Welch t-test:

On data averaged by Mouse.
Data is assumed heteroscedastic in relation to `Condition`.

```{r}
DAPI_Density_P12_mod_Nb_Area_agg <- afex::mixed(
  Nb_Area ~ Condition + (0 + dCondition | ID),
  data = DAPI_Density_P12_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(DAPI_Density_P12_mod_Nb_Area_agg$full_model, effects = "fixed", ci_method = "wald", drop = "Intercept")
```


<!------------------------------------------------------------------------------>
### GLMM:

**Gaussian:**

```{r}
DAPI_Density_P12_mod_Nb_Area_gauss <- glmmTMB(
  Nb_Area ~ Condition * Layer + (1 | Mouse),
  family = gaussian("log"),
  data = DAPI_Density_P12_data,
  REML = T
)

parameters(DAPI_Density_P12_mod_Nb_Area_gauss)
cat("\n")
performance(DAPI_Density_P12_mod_Nb_Area_gauss)
```

**Gamma:**

```{r}
DAPI_Density_P12_mod_Nb_Area_gamma <- glmmTMB(
  Nb_Area ~ Condition * Layer + (1 | Mouse),
  family = Gamma("log"),
  data = DAPI_Density_P12_data,
  REML = T
)

parameters(DAPI_Density_P12_mod_Nb_Area_gamma)
cat("\n")
performance(DAPI_Density_P12_mod_Nb_Area_gamma)
```

<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(DAPI_Density_P12_mod_Nb_Area_gauss, DAPI_Density_P12_mod_Nb_Area_gamma)
```

Best model:

```{r}
DAPI_Density_P12_mod_Nb_Area <- DAPI_Density_P12_mod_Nb_Area_gamma
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 10}
make_acf_plot(DAPI_Density_P12_mod_Nb_Area)

performance::check_model(DAPI_Density_P12_mod_Nb_Area, detrend = TRUE)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

DAPI_Density_P12_mod_Nb_Area_dharma <- DHARMa::simulateResiduals(DAPI_Density_P12_mod_Nb_Area, plot = F, n = nsim, seed = getOption("seed"))
DAPI_Density_P12_mod_Nb_Area_dharma_t <- DAPI_Density_P12_mod_Nb_Area_dharma$simulatedResponse |> t()
```

```{r fig.width = 10}
ppc_plots(DAPI_Density_P12_mod_Nb_Area, DAPI_Density_P12_mod_Nb_Area_dharma_t, term = "Condition")
ppc_plots(DAPI_Density_P12_mod_Nb_Area, DAPI_Density_P12_mod_Nb_Area_dharma_t, term = "Layer")
```

```{r fig.width = 10}
ppc_stat_plots(DAPI_Density_P12_mod_Nb_Area, DAPI_Density_P12_mod_Nb_Area_dharma_t, term = "Condition")
ppc_stat_plots(DAPI_Density_P12_mod_Nb_Area, DAPI_Density_P12_mod_Nb_Area_dharma_t, term = "Layer")
```

**Potential outliers:**

```{r}
insight::get_data(DAPI_Density_P12_mod_Nb_Area) |> 
  filter(!is.na(Nb_Area)) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(DAPI_Density_P12_mod_Nb_Area_dharma))
```


<!------------------------------------------------------------------------------>
## 4. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::parameters(
  DAPI_Density_P12_mod_Nb_Area, exponentiate = should_exp(DAPI_Density_P12_mod_Nb_Area), 
  ci_method = "wald", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(DAPI_Density_P12_mod_Nb_Area, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(DAPI_Density_P12_mod_Nb_Area, pred = "Condition")
```


<!------------------------------------------------------------------------------>
### Marginal Effects:

**Condition**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(DAPI_Density_P12_mod_Nb_Area), dvs = insight::find_response(DAPI_Density_P12_mod_Nb_Area), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Area, specs = "Condition", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Area, specs = "Condition", type = "response") |>
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Area, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 5, fig.height = 8}
make_signif_boxplot(DAPI_Density_P12_mod_Nb_Area, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_Density_P12_mod_Nb_Area)}] Boxplots - by [Condition]"), subfolder = DAPI_Density_P12_target, dpi = dpi_save_png, width = 5, height = 8)
```

**Layer**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(DAPI_Density_P12_mod_Nb_Area), dvs = insight::find_response(DAPI_Density_P12_mod_Nb_Area), between = "Layer")

log.main("===[Emmeans]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Area, specs = "Layer", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Area, specs = "Layer", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Area, specs = "Layer", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 3, fig.height = 5}
make_signif_boxplot(DAPI_Density_P12_mod_Nb_Area, xaxis = "Layer") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_Density_P12_mod_Nb_Area)}] Boxplots - by [Layer]"), subfolder = DAPI_Density_P12_target, dpi = dpi_save_png, width = 5, height = 8)
```

**Condition:Layer**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(DAPI_Density_P12_mod_Nb_Area), dvs = insight::find_response(DAPI_Density_P12_mod_Nb_Area), between = c("Layer", "Condition"))

log.main("===[Emmeans]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Area, specs = ~ Condition | Layer, type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Area, specs = ~ Condition | Layer, type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Area, specs = ~ Condition | Layer, type = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Area, specs = ~ Condition | Layer, trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Area, specs = ~ Condition | Layer, trans = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)
```

Plots:

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot(DAPI_Density_P12_mod_Nb_Area, xaxis = "Condition", facet = "Layer") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_Density_P12_mod_Nb_Area)}] Boxplots - by [Condition] within [Layer]"), subfolder = DAPI_Density_P12_target, dpi = dpi_save_png, width = 6, height = 5)
```

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot_inter(DAPI_Density_P12_mod_Nb_Area, xaxis = "Condition", facet = "Layer") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_Density_P12_mod_Nb_Area)}] Interaction Boxplots - by [Condition] within [Layer]"), subfolder = DAPI_Density_P12_target, dpi = dpi_save_png, width = 6, height = 5)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# III. Nb_Vol:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distributions:

**By Condition:**

```{r}
distribution_summary(DAPI_Density_P12_data, dvs = "Nb_Vol", between = "Condition")
```

```{r}
hist_plot(DAPI_Density_P12_data, var = "Nb_Vol", facet = "Condition")
```

**By Layer:**

```{r}
distribution_summary(DAPI_Density_P12_data, dvs = "Nb_Vol", between = "Layer")
```

```{r}
hist_plot(DAPI_Density_P12_data, var = "Nb_Vol", facet = "Layer")
```

**By Condition:Layer:**

```{r}
distribution_summary(DAPI_Density_P12_data, dvs = "Nb_Vol", between = c("Condition", "Layer"))
```

```{r}
hist_plot(DAPI_Density_P12_data, var = "Nb_Vol") + facet_grid(rows = vars(Layer), cols = vars(Condition))
```


<!------------------------------------------------------------------------------>
## 2. Models:
***

<!------------------------------------------------------------------------------>
### Welch t-test:

On data averaged by Mouse.
Data is assumed heteroscedastic in relation to `Condition`.

```{r}
DAPI_Density_P12_mod_Nb_Vol_agg <- afex::mixed(
  Nb_Vol ~ Condition + (0 + dCondition | ID),
  data = DAPI_Density_P12_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(DAPI_Density_P12_mod_Nb_Vol_agg$full_model, effects = "fixed", ci_method = "wald", drop = "Intercept")
```


<!------------------------------------------------------------------------------>
### GLMM:

**Gaussian:**

```{r}
DAPI_Density_P12_mod_Nb_Vol_gauss <- glmmTMB(
  Nb_Vol ~ Condition * Layer + (1 | Mouse),
  family = gaussian("log"),
  data = DAPI_Density_P12_data,
  REML = T
)

parameters(DAPI_Density_P12_mod_Nb_Vol_gauss)
cat("\n")
performance(DAPI_Density_P12_mod_Nb_Vol_gauss)
```

**Gamma:**

```{r}
DAPI_Density_P12_mod_Nb_Vol_gamma <- glmmTMB(
  Nb_Vol ~ Condition * Layer + (1 | Mouse),
  family = Gamma("log"),
  data = DAPI_Density_P12_data,
  REML = T
)

parameters(DAPI_Density_P12_mod_Nb_Vol_gamma)
cat("\n")
performance(DAPI_Density_P12_mod_Nb_Vol_gamma)
```

<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(DAPI_Density_P12_mod_Nb_Vol_gauss, DAPI_Density_P12_mod_Nb_Vol_gamma)
```

Best model:

```{r}
DAPI_Density_P12_mod_Nb_Vol <- DAPI_Density_P12_mod_Nb_Vol_gamma
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 10}
make_acf_plot(DAPI_Density_P12_mod_Nb_Vol)

performance::check_model(DAPI_Density_P12_mod_Nb_Vol, detrend = TRUE)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

DAPI_Density_P12_mod_Nb_Vol_dharma <- DHARMa::simulateResiduals(DAPI_Density_P12_mod_Nb_Vol, plot = F, n = nsim, seed = getOption("seed"))
DAPI_Density_P12_mod_Nb_Vol_dharma_t <- DAPI_Density_P12_mod_Nb_Vol_dharma$simulatedResponse |> t()
```

```{r fig.width = 10}
ppc_plots(DAPI_Density_P12_mod_Nb_Vol, DAPI_Density_P12_mod_Nb_Vol_dharma_t, term = "Condition")
ppc_plots(DAPI_Density_P12_mod_Nb_Vol, DAPI_Density_P12_mod_Nb_Vol_dharma_t, term = "Layer")
```

```{r fig.width = 10}
ppc_stat_plots(DAPI_Density_P12_mod_Nb_Vol, DAPI_Density_P12_mod_Nb_Vol_dharma_t, term = "Condition")
ppc_stat_plots(DAPI_Density_P12_mod_Nb_Vol, DAPI_Density_P12_mod_Nb_Vol_dharma_t, term = "Layer")
```

**Potential outliers:**

```{r}
insight::get_data(DAPI_Density_P12_mod_Nb_Vol) |> 
  filter(!is.na(Nb_Vol)) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(DAPI_Density_P12_mod_Nb_Vol_dharma))
```


<!------------------------------------------------------------------------------>
## 4. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::parameters(
  DAPI_Density_P12_mod_Nb_Vol, exponentiate = should_exp(DAPI_Density_P12_mod_Nb_Vol), 
  ci_method = "wald", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(DAPI_Density_P12_mod_Nb_Vol, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(DAPI_Density_P12_mod_Nb_Vol, pred = "Condition")
```


<!------------------------------------------------------------------------------>
### Marginal Effects:

**Condition**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(DAPI_Density_P12_mod_Nb_Vol), dvs = insight::find_response(DAPI_Density_P12_mod_Nb_Vol), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Vol, specs = "Condition", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Vol, specs = "Condition", type = "response") |>
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Vol, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 5, fig.height = 8}
make_signif_boxplot(DAPI_Density_P12_mod_Nb_Vol, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_Density_P12_mod_Nb_Vol)}] Boxplots - by [Condition]"), subfolder = DAPI_Density_P12_target, dpi = dpi_save_png, width = 5, height = 8)
```

**Layer**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(DAPI_Density_P12_mod_Nb_Vol), dvs = insight::find_response(DAPI_Density_P12_mod_Nb_Vol), between = "Layer")

log.main("===[Emmeans]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Vol, specs = "Layer", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Vol, specs = "Layer", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Vol, specs = "Layer", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 3, fig.height = 5}
make_signif_boxplot(DAPI_Density_P12_mod_Nb_Vol, xaxis = "Layer") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_Density_P12_mod_Nb_Vol)}] Boxplots - by [Layer]"), subfolder = DAPI_Density_P12_target, dpi = dpi_save_png, width = 5, height = 8)
```

**Condition:Layer**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(DAPI_Density_P12_mod_Nb_Vol), dvs = insight::find_response(DAPI_Density_P12_mod_Nb_Vol), between = c("Layer", "Condition"))

log.main("===[Emmeans]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Vol, specs = ~ Condition | Layer, type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Vol, specs = ~ Condition | Layer, type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Vol, specs = ~ Condition | Layer, type = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Vol, specs = ~ Condition | Layer, trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Nb_Vol, specs = ~ Condition | Layer, trans = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)
```

Plots:

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot(DAPI_Density_P12_mod_Nb_Vol, xaxis = "Condition", facet = "Layer") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_Density_P12_mod_Nb_Vol)}] Boxplots - by [Condition] within [Layer]"), subfolder = DAPI_Density_P12_target, dpi = dpi_save_png, width = 6, height = 5)
```

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot_inter(DAPI_Density_P12_mod_Nb_Vol, xaxis = "Condition", facet = "Layer") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_Density_P12_mod_Nb_Vol)}] Interaction Boxplots - by [Condition] within [Layer]"), subfolder = DAPI_Density_P12_target, dpi = dpi_save_png, width = 6, height = 5)
```



<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# IV. Avg_Distance:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distributions:

**By Condition:**

```{r}
distribution_summary(DAPI_Density_P12_data, dvs = "Avg_Distance", between = "Condition")
```

```{r}
hist_plot(DAPI_Density_P12_data, var = "Avg_Distance", facet = "Condition")
```

**By Layer:**

```{r}
distribution_summary(DAPI_Density_P12_data, dvs = "Avg_Distance", between = "Layer")
```

```{r}
hist_plot(DAPI_Density_P12_data, var = "Avg_Distance", facet = "Layer")
```

**By Condition:Layer:**

```{r}
distribution_summary(DAPI_Density_P12_data, dvs = "Avg_Distance", between = c("Condition", "Layer"))
```

```{r}
hist_plot(DAPI_Density_P12_data, var = "Avg_Distance") + facet_grid(rows = vars(Layer), cols = vars(Condition))
```


<!------------------------------------------------------------------------------>
## 2. Models:
***

<!------------------------------------------------------------------------------>
### Welch t-test:

On data averaged by Mouse.
Data is assumed heteroscedastic in relation to `Condition`.

```{r}
DAPI_Density_P12_mod_Avg_Distance_agg <- afex::mixed(
  Avg_Distance ~ Condition + (0 + dCondition | ID),
  data = DAPI_Density_P12_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(DAPI_Density_P12_mod_Avg_Distance_agg$full_model, effects = "fixed", ci_method = "wald", drop = "Intercept")
```


<!------------------------------------------------------------------------------>
### GLMM:

**Gaussian:**

```{r}
DAPI_Density_P12_mod_Avg_Distance_gauss <- glmmTMB(
  Avg_Distance ~ Condition * Layer + (1 | Mouse),
  family = gaussian("log"),
  data = DAPI_Density_P12_data,
  REML = T
)

parameters(DAPI_Density_P12_mod_Avg_Distance_gauss)
cat("\n")
performance(DAPI_Density_P12_mod_Avg_Distance_gauss)
```

**Gamma:**

```{r}
DAPI_Density_P12_mod_Avg_Distance_gamma <- glmmTMB(
  Avg_Distance ~ Condition * Layer + (1 | Mouse),
  family = Gamma("log"),
  data = DAPI_Density_P12_data,
  REML = T
)

parameters(DAPI_Density_P12_mod_Avg_Distance_gamma)
cat("\n")
performance(DAPI_Density_P12_mod_Avg_Distance_gamma)
```

<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(DAPI_Density_P12_mod_Avg_Distance_gauss, DAPI_Density_P12_mod_Avg_Distance_gamma)
```

Best model:

```{r}
DAPI_Density_P12_mod_Avg_Distance <- DAPI_Density_P12_mod_Avg_Distance_gamma
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 10}
make_acf_plot(DAPI_Density_P12_mod_Avg_Distance)

performance::check_model(DAPI_Density_P12_mod_Avg_Distance, detrend = TRUE)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

DAPI_Density_P12_mod_Avg_Distance_dharma <- DHARMa::simulateResiduals(DAPI_Density_P12_mod_Avg_Distance, plot = F, n = nsim, seed = getOption("seed"))
DAPI_Density_P12_mod_Avg_Distance_dharma_t <- DAPI_Density_P12_mod_Avg_Distance_dharma$simulatedResponse |> t()
```

```{r fig.width = 10}
ppc_plots(DAPI_Density_P12_mod_Avg_Distance, DAPI_Density_P12_mod_Avg_Distance_dharma_t, term = "Condition")
ppc_plots(DAPI_Density_P12_mod_Avg_Distance, DAPI_Density_P12_mod_Avg_Distance_dharma_t, term = "Layer")
```

```{r fig.width = 10}
ppc_stat_plots(DAPI_Density_P12_mod_Avg_Distance, DAPI_Density_P12_mod_Avg_Distance_dharma_t, term = "Condition")
ppc_stat_plots(DAPI_Density_P12_mod_Avg_Distance, DAPI_Density_P12_mod_Avg_Distance_dharma_t, term = "Layer")
```

**Potential outliers:**

```{r}
insight::get_data(DAPI_Density_P12_mod_Avg_Distance) |> 
  filter(!is.na(Avg_Distance)) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(DAPI_Density_P12_mod_Avg_Distance_dharma))
```


<!------------------------------------------------------------------------------>
## 4. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::parameters(
  DAPI_Density_P12_mod_Avg_Distance, exponentiate = should_exp(DAPI_Density_P12_mod_Avg_Distance), 
  ci_method = "wald", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(DAPI_Density_P12_mod_Avg_Distance, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(DAPI_Density_P12_mod_Avg_Distance, pred = "Condition")
```


<!------------------------------------------------------------------------------>
### Marginal Effects:

**Condition**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(DAPI_Density_P12_mod_Avg_Distance), dvs = insight::find_response(DAPI_Density_P12_mod_Avg_Distance), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Avg_Distance, specs = "Condition", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Avg_Distance, specs = "Condition", type = "response") |>
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Avg_Distance, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 5, fig.height = 8}
make_signif_boxplot(DAPI_Density_P12_mod_Avg_Distance, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_Density_P12_mod_Avg_Distance)}] Boxplots - by [Condition]"), subfolder = DAPI_Density_P12_target, dpi = dpi_save_png, width = 5, height = 8)
```

**Layer**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(DAPI_Density_P12_mod_Avg_Distance), dvs = insight::find_response(DAPI_Density_P12_mod_Avg_Distance), between = "Layer")

log.main("===[Emmeans]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Avg_Distance, specs = "Layer", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Avg_Distance, specs = "Layer", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Avg_Distance, specs = "Layer", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 3, fig.height = 5}
(make_signif_boxplot(DAPI_Density_P12_mod_Avg_Distance, xaxis = "Layer") + scale_color_viridis_d()) |> 
  save_png(filename = glue("[{get_model_tag(DAPI_Density_P12_mod_Avg_Distance)}] Boxplots - by [Layer]"), subfolder = DAPI_Density_P12_target, dpi = dpi_save_png, width = 5, height = 8)
```

**Condition:Layer**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(DAPI_Density_P12_mod_Avg_Distance), dvs = insight::find_response(DAPI_Density_P12_mod_Avg_Distance), between = c("Layer", "Condition"))

log.main("===[Emmeans]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Avg_Distance, specs = ~ Condition | Layer, type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Avg_Distance, specs = ~ Condition | Layer, type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Avg_Distance, specs = ~ Condition | Layer, type = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Avg_Distance, specs = ~ Condition | Layer, trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(DAPI_Density_P12_mod_Avg_Distance, specs = ~ Condition | Layer, trans = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)
```

Plots:

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot(DAPI_Density_P12_mod_Avg_Distance, xaxis = "Condition", facet = "Layer") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_Density_P12_mod_Avg_Distance)}] Boxplots - by [Condition] within [Layer]"), subfolder = DAPI_Density_P12_target, dpi = dpi_save_png, width = 6, height = 5)
```

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot_inter(DAPI_Density_P12_mod_Avg_Distance, xaxis = "Condition", facet = "Layer") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_Density_P12_mod_Avg_Distance)}] Interaction Boxplots - by [Condition] within [Layer]"), subfolder = DAPI_Density_P12_target, dpi = dpi_save_png, width = 6, height = 5)
```


