```{r include = F, echo = F}
source("../src/init.R", echo = F)
```

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# I. Data:
***

```{r data}

DAPI_ML_Ad_target <- "DAPI_ML_Adult"

(DAPI_ML_Ad_data <- load_dapi_ml_ad(config$data$dapi_ml_ad_path))

### Variables:

DAPI_ML_Ad_responses <- c("A_ML", "A_DAPI", "Vol_DAPI")
DAPI_ML_Ad_predictors <- c("Condition", "Z", "Mouse")

A_ML_name <- "Molecular layer area *(10^(-4) μm^(2))*"
A_DAPI_name <- "Area marked with DAPI *(10^(-4) μm^(2))*"
Vol_DAPI_name <- "Volume of DAPI marking *(10^(-4) μm^(3))*"

contrasts(DAPI_ML_Ad_data$Condition) <- contr.sum
contrasts(DAPI_ML_Ad_data$Z) <- contr.sum

### Averaged data:

DAPI_ML_Ad_data_agg <- DAPI_ML_Ad_data |> 
  group_by(Mouse, Condition) |> 
  summarize(across(matches(DAPI_ML_Ad_responses), .fns = \(.x) mean(.x, na.rm = T))) |> 
  ungroup() |> 
  mutate(dCondition = as.numeric(Condition == "IH")) |> 
  rowid_to_column("ID")
```

```{r}
DAPI_ML_Ad_data %>% filter_all(any_vars(is.na(.)))
```


<!------------------------------------------------------------------------------>
## Correlations:
***

```{r fig.width = 8}
corr_matrix_plot(DAPI_ML_Ad_data, vars = c(DAPI_ML_Ad_predictors, DAPI_ML_Ad_responses))
```

```{r fig.width = 10}
GGally::ggpairs(
  DAPI_ML_Ad_data, columns = c(DAPI_ML_Ad_predictors, DAPI_ML_Ad_responses), 
  mapping = aes(color = Condition), lower = list(continuous = "smooth")
)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# II. A_ML:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distributions:

**By Condition:**

```{r}
distribution_summary(DAPI_ML_Ad_data, dvs = "A_ML", between = "Condition")
```

```{r}
hist_plot(DAPI_ML_Ad_data, var = "A_ML", facet = "Condition")
```

**By Z:**

```{r}
distribution_summary(DAPI_ML_Ad_data, dvs = "A_ML", between = "Z")
```

```{r}
hist_plot(DAPI_ML_Ad_data, var = "A_ML", facet = "Z")
```

**By Condition:Z:**

```{r}
distribution_summary(DAPI_ML_Ad_data, dvs = "A_ML", between = c("Condition", "Z"))
```

```{r}
hist_plot(DAPI_ML_Ad_data, var = "A_ML") + facet_grid(rows = vars(Z), cols = vars(Condition))
```


<!------------------------------------------------------------------------------>
## 2. Models:
***

<!------------------------------------------------------------------------------>
### Welch t-test:

On data averaged by Mouse.
Data is assumed heteroscedastic in relation to `Condition`.

```{r}
DAPI_ML_Ad_mod_A_ML_agg <- afex::mixed(
  A_ML ~ Condition + (0 + dCondition | ID),
  data = DAPI_ML_Ad_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(DAPI_ML_Ad_mod_A_ML_agg$full_model, effects = "fixed", ci_method = "wald", drop = "Intercept")
```


<!------------------------------------------------------------------------------>
### GLMM:

**Gaussian:**

```{r}
DAPI_ML_Ad_mod_A_ML_gauss <- glmmTMB(
  A_ML ~ Condition * Z + (1 | Mouse),
  family = gaussian("log"),
  data = DAPI_ML_Ad_data,
  REML = T
)

parameters(DAPI_ML_Ad_mod_A_ML_gauss)
cat("\n")
performance(DAPI_ML_Ad_mod_A_ML_gauss)
```

**Gamma:**

```{r}
DAPI_ML_Ad_mod_A_ML_gamma <- glmmTMB(
  A_ML ~ Condition * Z + (1 | Mouse),
  family = Gamma("log"),
  data = DAPI_ML_Ad_data,
  REML = T
)

parameters(DAPI_ML_Ad_mod_A_ML_gamma)
cat("\n")
performance(DAPI_ML_Ad_mod_A_ML_gamma)
```

<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(DAPI_ML_Ad_mod_A_ML_gauss, DAPI_ML_Ad_mod_A_ML_gamma)
```

Best model:

```{r}
DAPI_ML_Ad_mod_A_ML <- DAPI_ML_Ad_mod_A_ML_gamma
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 10}
make_acf_plot(DAPI_ML_Ad_mod_A_ML)

performance::check_model(DAPI_ML_Ad_mod_A_ML, detrend = TRUE)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

DAPI_ML_Ad_mod_A_ML_dharma <- DHARMa::simulateResiduals(DAPI_ML_Ad_mod_A_ML, plot = F, n = nsim, seed = getOption("seed"))
DAPI_ML_Ad_mod_A_ML_dharma_t <- DAPI_ML_Ad_mod_A_ML_dharma$simulatedResponse |> t()
```

```{r fig.width = 10}
ppc_plots(DAPI_ML_Ad_mod_A_ML, DAPI_ML_Ad_mod_A_ML_dharma_t, term = "Condition")
ppc_plots(DAPI_ML_Ad_mod_A_ML, DAPI_ML_Ad_mod_A_ML_dharma_t, term = "Z")
```

```{r fig.width = 10}
ppc_stat_plots(DAPI_ML_Ad_mod_A_ML, DAPI_ML_Ad_mod_A_ML_dharma_t, term = "Condition")
ppc_stat_plots(DAPI_ML_Ad_mod_A_ML, DAPI_ML_Ad_mod_A_ML_dharma_t, term = "Z")
```

**Potential outliers:**

```{r}
insight::get_data(DAPI_ML_Ad_mod_A_ML) |> 
  filter(!is.na(A_ML)) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(DAPI_ML_Ad_mod_A_ML_dharma))
```


<!------------------------------------------------------------------------------>
## 4. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::parameters(
  DAPI_ML_Ad_mod_A_ML, exponentiate = should_exp(DAPI_ML_Ad_mod_A_ML), 
  ci_method = "wald", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(DAPI_ML_Ad_mod_A_ML, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(DAPI_ML_Ad_mod_A_ML, pred = "Condition")
```


<!------------------------------------------------------------------------------>
### Marginal Effects:

**Condition**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(DAPI_ML_Ad_mod_A_ML), dvs = insight::find_response(DAPI_ML_Ad_mod_A_ML), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_ML, specs = "Condition", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_ML, specs = "Condition", type = "response") |>
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_ML, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 5, fig.height = 8}
make_signif_boxplot(DAPI_ML_Ad_mod_A_ML, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_ML_Ad_mod_A_ML)}] Boxplots - by [Condition]"), subfolder = DAPI_ML_Ad_target, dpi = 600, width = 5, height = 8)
```

**Z**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(DAPI_ML_Ad_mod_A_ML), dvs = insight::find_response(DAPI_ML_Ad_mod_A_ML), between = "Z")

log.main("===[Emmeans]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_ML, specs = "Z", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_ML, specs = "Z", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_ML, specs = "Z", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 3, fig.height = 5}
(make_signif_boxplot(DAPI_ML_Ad_mod_A_ML, xaxis = "Z") + scale_color_viridis_d()) |> 
  save_png(filename = glue("[{get_model_tag(DAPI_ML_Ad_mod_A_ML)}] Boxplots - by [Z]"), subfolder = DAPI_ML_Ad_target, dpi = 600, width = 5, height = 8)
```

**Condition:Z**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(DAPI_ML_Ad_mod_A_ML), dvs = insight::find_response(DAPI_ML_Ad_mod_A_ML), between = c("Z", "Condition"))

log.main("===[Emmeans]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_ML, specs = ~ Condition | Z, type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_ML, specs = ~ Condition | Z, type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_ML, specs = ~ Condition | Z, type = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_ML, specs = ~ Condition | Z, trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_ML, specs = ~ Condition | Z, trans = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)
```

Plots:

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot(DAPI_ML_Ad_mod_A_ML, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_ML_Ad_mod_A_ML)}] Boxplots - by [Condition] within [Z]"), subfolder = DAPI_ML_Ad_target, dpi = 600, width = 6, height = 5)
```

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot_inter(DAPI_ML_Ad_mod_A_ML, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_ML_Ad_mod_A_ML)}] Interaction Boxplots - by [Condition] within [Z]"), subfolder = DAPI_ML_Ad_target, dpi = 600, width = 6, height = 5)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# III. A_DAPI:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distributions:

**By Condition:**

```{r}
distribution_summary(DAPI_ML_Ad_data, dvs = str_subset(DAPI_ML_Ad_responses, "A_DAPI"), between = "Condition")
```

```{r fig.width = 6}
purrr::map(
  str_subset(DAPI_ML_Ad_responses, "A_DAPI"),
  \(.x) hist_plot(DAPI_ML_Ad_data, var = .x, facet = "Condition")
)
```

**By Z:**

```{r}
distribution_summary(DAPI_ML_Ad_data, dvs = str_subset(DAPI_ML_Ad_responses, "A_DAPI"), between = "Z")
```

```{r fig.width = 6}
purrr::map(
  str_subset(DAPI_ML_Ad_responses, "A_DAPI"),
  \(.x) hist_plot(DAPI_ML_Ad_data, var = .x, facet = "Z") + scale_fill_viridis_d() + scale_color_viridis_d()
)
```

**By Condition:Z:**

```{r}
distribution_summary(DAPI_ML_Ad_data, dvs = str_subset(DAPI_ML_Ad_responses, "A_DAPI"), between = c("Condition", "Z"))
```

```{r fig.width = 6}
purrr::map(
  str_subset(DAPI_ML_Ad_responses, "A_DAPI"),
  \(.x) hist_plot(DAPI_ML_Ad_data, var = .x) + facet_grid(rows = vars(Z), cols = vars(Condition))
)
```



<!------------------------------------------------------------------------------>
## 2. Models:
***

<!------------------------------------------------------------------------------>
### Welch t-test:

On data averaged by Mouse.
Data is assumed heteroscedastic in relation to `Condition`.

```{r}
DAPI_ML_Ad_mod_A_DAPI_agg <- afex::mixed(
  A_DAPI ~ Condition + (0 + dCondition | ID),
  data = DAPI_ML_Ad_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(DAPI_ML_Ad_mod_A_DAPI_agg$full_model, effects = "fixed", ci_method = "wald", drop = "Intercept")
```


<!------------------------------------------------------------------------------>
### GLMM:

**Gaussian:**

```{r}
DAPI_ML_Ad_mod_A_DAPI_gauss <- glmmTMB(
  A_DAPI ~ Condition * Z + (1 | Mouse),
  family = gaussian("log"),
  data = DAPI_ML_Ad_data,
  REML = T
)

parameters(DAPI_ML_Ad_mod_A_DAPI_gauss)
cat("\n")
performance(DAPI_ML_Ad_mod_A_DAPI_gauss)
```

**Gamma:**

```{r}
DAPI_ML_Ad_mod_A_DAPI_gamma <- glmmTMB(
  A_DAPI ~ Condition * Z + (1 | Mouse),
  family = Gamma("log"),
  data = DAPI_ML_Ad_data,
  REML = T
)

parameters(DAPI_ML_Ad_mod_A_DAPI_gamma)
cat("\n")
performance(DAPI_ML_Ad_mod_A_DAPI_gamma)
```


<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(DAPI_ML_Ad_mod_A_DAPI_gauss, DAPI_ML_Ad_mod_A_DAPI_gamma)
```

Best model:

```{r}
DAPI_ML_Ad_mod_A_DAPI <- DAPI_ML_Ad_mod_A_DAPI_gamma
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 10}
make_acf_plot(DAPI_ML_Ad_mod_A_DAPI)

performance::check_model(DAPI_ML_Ad_mod_A_DAPI, detrend = TRUE)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

DAPI_ML_Ad_mod_A_DAPI_dharma <- DHARMa::simulateResiduals(DAPI_ML_Ad_mod_A_DAPI, plot = F, n = nsim, seed = getOption("seed"))
DAPI_ML_Ad_mod_A_DAPI_dharma_t <- DAPI_ML_Ad_mod_A_DAPI_dharma$simulatedResponse |> t()
```

```{r fig.width = 10}
ppc_plots(DAPI_ML_Ad_mod_A_DAPI, DAPI_ML_Ad_mod_A_DAPI_dharma_t, term = "Condition")
ppc_plots(DAPI_ML_Ad_mod_A_DAPI, DAPI_ML_Ad_mod_A_DAPI_dharma_t, term = "Z")
```

```{r fig.width = 10}
ppc_stat_plots(DAPI_ML_Ad_mod_A_DAPI, DAPI_ML_Ad_mod_A_DAPI_dharma_t, term = "Condition")
ppc_stat_plots(DAPI_ML_Ad_mod_A_DAPI, DAPI_ML_Ad_mod_A_DAPI_dharma_t, term = "Z")
```

**Potential outliers:**

```{r}
insight::get_data(DAPI_ML_Ad_mod_A_DAPI) |> 
  filter(!is.na(A_DAPI)) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(DAPI_ML_Ad_mod_A_DAPI_dharma))
```


<!------------------------------------------------------------------------------>
## 4. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::parameters(
  DAPI_ML_Ad_mod_A_DAPI, exponentiate = should_exp(DAPI_ML_Ad_mod_A_DAPI), 
  ci_method = "wald", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(DAPI_ML_Ad_mod_A_DAPI, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(DAPI_ML_Ad_mod_A_DAPI, pred = "Condition")
```

<!------------------------------------------------------------------------------>
### Marginal Effects:

**Condition**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(DAPI_ML_Ad_mod_A_DAPI), dvs = insight::find_response(DAPI_ML_Ad_mod_A_DAPI), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_DAPI, specs = "Condition", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_DAPI, specs = "Condition", type = "response") |>
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_DAPI, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 5, fig.height = 8}
make_signif_boxplot(DAPI_ML_Ad_mod_A_DAPI, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_ML_Ad_mod_A_DAPI)}] Boxplots - by [Condition]"), subfolder = DAPI_ML_Ad_target, dpi = 600, width = 5, height = 8)
```

**Z**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(DAPI_ML_Ad_mod_A_DAPI), dvs = insight::find_response(DAPI_ML_Ad_mod_Vol_DAPI), between = "Z")

log.main("===[Emmeans]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_DAPI, specs = "Z", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_DAPI, specs = "Z", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_DAPI, specs = "Z", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 3, fig.height = 5}
(make_signif_boxplot(DAPI_ML_Ad_mod_A_DAPI, xaxis = "Z") + scale_color_viridis_d()) |> 
  save_png(filename = glue("[{get_model_tag(DAPI_ML_Ad_mod_A_DAPI)}] Boxplots - by [Z]"), subfolder = DAPI_ML_Ad_target, dpi = 600, width = 5, height = 8)
```

**Condition:Z**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(DAPI_ML_Ad_mod_A_DAPI), dvs = insight::find_response(DAPI_ML_Ad_mod_A_DAPI), between = c("Z", "Condition"))

log.main("===[Emmeans]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_DAPI, specs = ~ Condition | Z, type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_DAPI, specs = ~ Condition | Z, type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_DAPI, specs = ~ Condition | Z, type = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_DAPI, specs = ~ Condition | Z, trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_A_DAPI, specs = ~ Condition | Z, trans = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)
```

Plots:

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot(DAPI_ML_Ad_mod_A_DAPI, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_ML_Ad_mod_A_DAPI)}] Boxplots - by [Condition] within [Z]"), subfolder = DAPI_ML_Ad_target, dpi = 600, width = 6, height = 5)
```

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot_inter(DAPI_ML_Ad_mod_A_DAPI, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_ML_Ad_mod_A_DAPI)}] Interaction Boxplots - by [Condition] within [Z]"), subfolder = DAPI_ML_Ad_target, dpi = 600, width = 6, height = 5)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# IV. Vol_DAPI:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distributions:

**By Condition:**

```{r}
distribution_summary(DAPI_ML_Ad_data, dvs = str_subset(DAPI_ML_Ad_responses, "A_DAPI"), between = "Condition")
```

```{r fig.width = 6}
purrr::map(
  str_subset(DAPI_ML_Ad_responses, "A_DAPI"),
  \(.x) hist_plot(DAPI_ML_Ad_data, var = .x, facet = "Condition")
)
```

**By Z:**

```{r}
distribution_summary(DAPI_ML_Ad_data, dvs = str_subset(DAPI_ML_Ad_responses, "A_DAPI"), between = "Z")
```

```{r fig.width = 6}
purrr::map(
  str_subset(DAPI_ML_Ad_responses, "A_DAPI"),
  \(.x) hist_plot(DAPI_ML_Ad_data, var = .x, facet = "Z") + scale_fill_viridis_d() + scale_color_viridis_d()
)
```

**By Condition:Z:**

```{r}
distribution_summary(DAPI_ML_Ad_data, dvs = str_subset(DAPI_ML_Ad_responses, "A_DAPI"), between = c("Condition", "Z"))
```

```{r fig.width = 6}
purrr::map(
  str_subset(DAPI_ML_Ad_responses, "A_DAPI"),
  \(.x) hist_plot(DAPI_ML_Ad_data, var = .x) + facet_grid(rows = vars(Z), cols = vars(Condition))
)
```


<!------------------------------------------------------------------------------>
## 2. Models:
***


<!------------------------------------------------------------------------------>
### Welch t-test:

On data averaged by Mouse.
Data is assumed heteroscedastic in relation to `Condition`.

```{r}
DAPI_ML_Ad_mod_Vol_DAPI_agg <- afex::mixed(
  Vol_DAPI ~ Condition + (0 + dCondition | ID),
  data = DAPI_ML_Ad_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(DAPI_ML_Ad_mod_Vol_DAPI_agg$full_model, effects = "fixed", ci_method = "wald", drop = "Intercept")
```


<!------------------------------------------------------------------------------>
### GLMM:

**Gaussian:**

```{r}
DAPI_ML_Ad_mod_Vol_DAPI_gauss <- glmmTMB(
  Vol_DAPI ~ Condition * Z + (1 | Mouse),
  family = gaussian("log"),
  data = DAPI_ML_Ad_data,
  REML = T
)

parameters(DAPI_ML_Ad_mod_Vol_DAPI_gauss)
cat("\n")
performance(DAPI_ML_Ad_mod_Vol_DAPI_gauss)
```

**Gamma:**

```{r}
DAPI_ML_Ad_mod_Vol_DAPI_gamma <- glmmTMB(
  Vol_DAPI ~ Condition * Z + (1 | Mouse),
  family = Gamma("log"),
  data = DAPI_ML_Ad_data,
  REML = T
)

parameters(DAPI_ML_Ad_mod_Vol_DAPI_gamma)
cat("\n")
performance(DAPI_ML_Ad_mod_Vol_DAPI_gamma)
```


<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(DAPI_ML_Ad_mod_Vol_DAPI_gauss, DAPI_ML_Ad_mod_Vol_DAPI_gamma)
```

Best model:

```{r}
DAPI_ML_Ad_mod_Vol_DAPI <- DAPI_ML_Ad_mod_Vol_DAPI_gamma
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 10}
performance::check_model(DAPI_ML_Ad_mod_Vol_DAPI, detrend = TRUE)

make_acf_plot(DAPI_ML_Ad_mod_Vol_DAPI)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

DAPI_ML_Ad_mod_Vol_DAPI_dharma <- DHARMa::simulateResiduals(DAPI_ML_Ad_mod_Vol_DAPI, plot = F, n = nsim, seed = getOption("seed"))
DAPI_ML_Ad_mod_Vol_DAPI_dharma_t <- DAPI_ML_Ad_mod_Vol_DAPI_dharma$simulatedResponse |> t()
```

```{r fig.width = 10}
ppc_plots(DAPI_ML_Ad_mod_Vol_DAPI, DAPI_ML_Ad_mod_Vol_DAPI_dharma_t, term = "Condition")
ppc_plots(DAPI_ML_Ad_mod_Vol_DAPI, DAPI_ML_Ad_mod_Vol_DAPI_dharma_t, term = "Z")
```

```{r fig.width = 10}
ppc_stat_plots(DAPI_ML_Ad_mod_Vol_DAPI, DAPI_ML_Ad_mod_Vol_DAPI_dharma_t, term = "Condition")
ppc_stat_plots(DAPI_ML_Ad_mod_Vol_DAPI, DAPI_ML_Ad_mod_Vol_DAPI_dharma_t, term = "Z")
```

**Potential outliers:**

```{r}
insight::get_data(DAPI_ML_Ad_mod_Vol_DAPI) |> 
  filter(!is.na(Vol_DAPI)) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(DAPI_ML_Ad_mod_Vol_DAPI_dharma))
```


<!------------------------------------------------------------------------------>
## 4. Effect Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::parameters(
  DAPI_ML_Ad_mod_Vol_DAPI, exponentiate = should_exp(DAPI_ML_Ad_mod_Vol_DAPI), 
  ci_method = "wald", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(DAPI_ML_Ad_mod_Vol_DAPI, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(DAPI_ML_Ad_mod_Vol_DAPI, pred = "Condition")
```


<!------------------------------------------------------------------------------>
### Marginal Effects:

**Condition**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(DAPI_ML_Ad_mod_Vol_DAPI), dvs = insight::find_response(DAPI_ML_Ad_mod_Vol_DAPI), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_Vol_DAPI, specs = "Condition", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_Vol_DAPI, specs = "Condition", type = "response") |>
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_Vol_DAPI, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 5, fig.height = 8}
make_signif_boxplot(DAPI_ML_Ad_mod_Vol_DAPI, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_ML_Ad_mod_Vol_DAPI)}] Boxplots - by [Condition]"), subfolder = DAPI_ML_Ad_target, dpi = 600, width = 5, height = 8)
```

**Z**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(DAPI_ML_Ad_mod_Vol_DAPI), dvs = insight::find_response(DAPI_ML_Ad_mod_Vol_DAPI), between = "Z")

log.main("===[Emmeans]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_Vol_DAPI, specs = "Z", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_Vol_DAPI, specs = "Z", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_Vol_DAPI, specs = "Z", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 3, fig.height = 5}
(make_signif_boxplot(DAPI_ML_Ad_mod_Vol_DAPI, xaxis = "Z") + scale_color_viridis_d()) |> 
  save_png(filename = glue("[{get_model_tag(DAPI_ML_Ad_mod_Vol_DAPI)}] Boxplots - by [Z]"), subfolder = DAPI_ML_Ad_target, dpi = 600, width = 5, height = 8)
```

**Condition:Z**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(DAPI_ML_Ad_mod_Vol_DAPI), dvs = insight::find_response(DAPI_ML_Ad_mod_Vol_DAPI), between = c("Z", "Condition"))

log.main("===[Emmeans]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_Vol_DAPI, specs = ~ Condition | Z, type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_Vol_DAPI, specs = ~ Condition | Z, type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_Vol_DAPI, specs = ~ Condition | Z, type = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_Vol_DAPI, specs = ~ Condition | Z, trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(DAPI_ML_Ad_mod_Vol_DAPI, specs = ~ Condition | Z, trans = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)
```

Plots:

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot(DAPI_ML_Ad_mod_Vol_DAPI, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_ML_Ad_mod_Vol_DAPI)}] Boxplots - by [Condition] within [Z]"), subfolder = DAPI_ML_Ad_target, dpi = 600, width = 6, height = 5)
```

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot_inter(DAPI_ML_Ad_mod_Vol_DAPI, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(DAPI_ML_Ad_mod_Vol_DAPI)}] Interaction Boxplots - by [Condition] within [Z]"), subfolder = DAPI_ML_Ad_target, dpi = 600, width = 6, height = 5)
```

