```{r include = F, echo = F}
source("../src/init.R", echo = F)
```

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# I. Data:
***

```{r data}

GluD2_target <- "GluD2"

(GluD2_data <- load_GluD2(config$data$GluD2_path) |> select(-N_CC))

### Variables:

GluD2_responses <- c("A_CL_GLUD2_DD_per_cell", "A_DD", "A_DD_per_cell", "A_GLUD2", "Vol_GLUD2")
GluD2_predictors <- c("Condition", "Z")

A_GLUD2_name <- "Gluð2-labelled Parallel fiber area  \n in the ML *(10^(-5) μm^(2))*"
Vol_GLUD2_name  <- "Gluð2-labelled Parallel fiber volume  \n in the ML *(10^(-5) μm^(3))*"

A_DD_name  <- "Purkinje dendrite area *(10^(-4) μm^(2))*"
A_DD_per_cell_name  <- "Purkinje dendrite area *(10^(-4) μm^(2))*  \n per Purkinje cell"


contrasts(GluD2_data$Condition) <- contr.sum
contrasts(GluD2_data$Z) <- contr.sum

### Averaged data:

GluD2_data_agg <- GluD2_data |> 
  group_by(Mouse, Condition) |> 
  summarize(across(matches(GluD2_responses), .fns = \(.x) mean(.x, na.rm = T))) |> 
  ungroup() |> 
  mutate(dCondition = as.numeric(Condition == "IH")) |> 
  rowid_to_column("ID")
```

```{r}
GluD2_data %>% filter_all(any_vars(is.na(.)))
```

<!------------------------------------------------------------------------------>
## Correlations:
***

```{r fig.width = 8}
corr_matrix_plot(GluD2_data, vars = c(GluD2_responses, GluD2_predictors))
```

```{r fig.width = 10}
GGally::ggpairs(
  GluD2_data, columns = c(GluD2_predictors, GluD2_responses), 
  mapping = aes(color = Condition), lower = list(continuous = "smooth")
)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# II. A_DD_per_cell:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distributions:

**By Condition:**

```{r}
distribution_summary(GluD2_data, dvs = "A_DD_per_cell", between = "Condition")
```

```{r}
hist_plot(GluD2_data, var = "A_DD_per_cell", facet = "Condition")
```

**By Z:**

```{r}
distribution_summary(GluD2_data, dvs = "A_DD_per_cell", between = "Z")
```

```{r}
hist_plot(GluD2_data, var = "A_DD_per_cell", facet = "Z")
```

**By Condition:Z:**

```{r}
distribution_summary(GluD2_data, dvs = "A_DD_per_cell", between = c("Condition", "Z"))
```

```{r}
hist_plot(GluD2_data, var = "A_DD_per_cell") + facet_grid(rows = vars(Z), cols = vars(Condition))
```


<!------------------------------------------------------------------------------>
## 2. Models:
***

<!------------------------------------------------------------------------------>
### Welch t-test:

On data aggregated by Mouse.
Data is assumed heteroscedastic in relation to `Condition`.

```{r}
GluD2_mod_A_DD_per_cell_agg <- afex::mixed(
  A_DD_per_cell ~ Condition + (0 + dCondition | ID),
  data = GluD2_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(GluD2_mod_A_DD_per_cell_agg$full_model, effects = "fixed", ci_method = "wald", drop = "Intercept")
```


<!------------------------------------------------------------------------------>
### GLMM:

**Gaussian:**

```{r}
GluD2_mod_A_DD_per_cell_gauss <- glmmTMB::glmmTMB(
  A_DD_per_cell ~ Condition * Z + (1 | Mouse),
  family = gaussian("log"),
  data = GluD2_data,
  REML = T
)

parameters::parameters(GluD2_mod_A_DD_per_cell_gauss)
cat("\n\n")
performance::performance(GluD2_mod_A_DD_per_cell_gauss)
```

**Gamma:**

```{r}
GluD2_mod_A_DD_per_cell_gamma <- glmmTMB::glmmTMB(
  A_DD_per_cell ~ Condition * Z + (1 | Mouse),
  family = Gamma("log"),
  data = GluD2_data,
  REML = T
)

parameters::parameters(GluD2_mod_A_DD_per_cell_gamma)
cat("\n\n")
performance::performance(GluD2_mod_A_DD_per_cell_gamma)
```


<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(GluD2_mod_A_DD_per_cell_gauss, GluD2_mod_A_DD_per_cell_gamma)
```

Best model:

```{r}
GluD2_mod_A_DD_per_cell <- GluD2_mod_A_DD_per_cell_gamma
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 8}
make_acf_plot(GluD2_mod_A_DD_per_cell)

performance::check_model(GluD2_mod_A_DD_per_cell, detrend = TRUE)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

GluD2_mod_A_DD_per_cell_dharma <- DHARMa::simulateResiduals(GluD2_mod_A_DD_per_cell, plot = F, n = nsim, seed = getOption("seed"))
GluD2_mod_A_DD_per_cell_dharma_t <- GluD2_mod_A_DD_per_cell_dharma$simulatedResponse |> t()
```

```{r fig.width = 10}
ppc_plots(GluD2_mod_A_DD_per_cell, simulations = GluD2_mod_A_DD_per_cell_dharma_t, term = "Condition")
ppc_plots(GluD2_mod_A_DD_per_cell, simulations = GluD2_mod_A_DD_per_cell_dharma_t, term = "Z")
```

```{r fig.width = 10}
ppc_stat_plots(GluD2_mod_A_DD_per_cell, simulations = GluD2_mod_A_DD_per_cell_dharma_t, term = "Condition")
ppc_stat_plots(GluD2_mod_A_DD_per_cell, simulations = GluD2_mod_A_DD_per_cell_dharma_t, term = "Z")
```

**Potential outliers:**

```{r fig.width = 10}
insight::get_data(GluD2_mod_A_DD_per_cell) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(GluD2_mod_A_DD_per_cell_dharma))
```



<!------------------------------------------------------------------------------>
## 4. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::parameters(
  GluD2_mod_A_DD_per_cell, exponentiate = should_exp(GluD2_mod_A_DD_per_cell), 
  ci_method = "Wald", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(GluD2_mod_A_DD_per_cell, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(GluD2_mod_A_DD_per_cell, pred = "Condition")
```

<!------------------------------------------------------------------------------>
### Marginal Effects:

**Condition:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(GluD2_mod_A_DD_per_cell), dvs = insight::find_response(GluD2_mod_A_DD_per_cell), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(GluD2_mod_A_DD_per_cell, specs = "Condition", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(GluD2_mod_A_DD_per_cell, specs = "Condition", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(GluD2_mod_A_DD_per_cell, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 4, fig.height = 7}
make_signif_boxplot(GluD2_mod_A_DD_per_cell, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(GluD2_mod_A_DD_per_cell)}] Boxplots - by [Condition]"), subfolder = GluD2_target, dpi = 600, width = 5, height = 8)
```

**Z:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(GluD2_mod_A_DD_per_cell), dvs = insight::find_response(GluD2_mod_A_DD_per_cell), between = "Z")

log.main("===[Emmeans]===\n")

emmeans::emmeans(GluD2_mod_A_DD_per_cell, specs = "Z", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(GluD2_mod_A_DD_per_cell, specs = "Z", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(GluD2_mod_A_DD_per_cell, specs = "Z", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 4, fig.height = 7}
make_signif_boxplot(GluD2_mod_A_DD_per_cell, xaxis = "Z") |> 
  save_png(filename = glue("[{get_model_tag(GluD2_mod_A_DD_per_cell)}] Boxplots - by [Z]"), subfolder = GluD2_target, dpi = 600, width = 4.5, height = 7)
```

**Condition:Z**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(GluD2_mod_A_DD_per_cell), dvs = insight::find_response(GluD2_mod_A_DD_per_cell), between = c("Condition", "Z"))

log.main("===[Emmeans]===\n")

emmeans::emmeans(GluD2_mod_A_DD_per_cell, specs = ~ Condition | Z, type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(GluD2_mod_A_DD_per_cell, specs = ~ Condition | Z, type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(GluD2_mod_A_DD_per_cell, specs = ~ Condition | Z, type = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(GluD2_mod_A_DD_per_cell, specs = ~ Condition | Z, trans = "response") |>
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(GluD2_mod_A_DD_per_cell, specs = ~ Condition | Z, trans = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)
```

Plots:

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot(GluD2_mod_A_DD_per_cell, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(GluD2_mod_A_DD_per_cell)}] Boxplots - by [Condition] within [Z]"), subfolder = GluD2_target, dpi = 600, width = 10, height = 7)
```

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot_inter(GluD2_mod_A_DD_per_cell, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(GluD2_mod_A_DD_per_cell)}] Interaction Boxplots - by [Condition] within [Z]"), subfolder = GluD2_target, dpi = 600, width = 10, height = 7)
```



<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# III. A_GLUD2:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distributions:

**By Condition:**

```{r}
distribution_summary(GluD2_data, dvs = "A_GLUD2", between = "Condition")
```

```{r}
hist_plot(GluD2_data, var = "A_GLUD2", facet = "Condition")
```

**By Z:**

```{r}
distribution_summary(GluD2_data, dvs = "A_GLUD2", between = "Z")
```

```{r}
hist_plot(GluD2_data, var = "A_GLUD2", facet = "Z")
```

**By Condition:Z:**

```{r}
distribution_summary(GluD2_data, dvs = "A_GLUD2", between = c("Condition", "Z"))
```

```{r}
hist_plot(GluD2_data, var = "A_GLUD2") + facet_grid(rows = vars(Z), cols = vars(Condition))
```


<!------------------------------------------------------------------------------>
## 2. Models:
***

<!------------------------------------------------------------------------------>
### Welch t-test:

On data aggregated by Mouse.
Data is assumed heteroscedastic in relation to `Condition`.

```{r}
GluD2_mod_A_GLUD2_agg <- afex::mixed(
  A_GLUD2 ~ Condition + (0 + dCondition | ID),
  data = GluD2_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(GluD2_mod_A_GLUD2_agg$full_model, effects = "fixed", ci_method = "wald", drop = "Intercept")
```


<!------------------------------------------------------------------------------>
### GLMM:

**Gaussian:**

```{r}
GluD2_mod_A_GLUD2_gauss <- glmmTMB::glmmTMB(
  A_GLUD2 ~ Condition * Z + (1 | Mouse),
  family = gaussian("log"),
  data = GluD2_data,
  REML = T
)

parameters::parameters(GluD2_mod_A_GLUD2_gauss)
cat("\n\n")
performance::performance(GluD2_mod_A_GLUD2_gauss)
```

**Gamma:**

```{r}
GluD2_mod_A_GLUD2_gamma <- glmmTMB::glmmTMB(
  A_GLUD2 ~ Condition * Z + (1 | Mouse),
  family = Gamma("log"),
  data = GluD2_data,
  REML = T
)

parameters::parameters(GluD2_mod_A_GLUD2_gamma)
cat("\n\n")
performance::performance(GluD2_mod_A_GLUD2_gamma)
```


<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(GluD2_mod_A_GLUD2_gauss, GluD2_mod_A_GLUD2_gamma)
```

Best model:

```{r}
GluD2_mod_A_GLUD2 <- GluD2_mod_A_GLUD2_gamma
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 8}
make_acf_plot(GluD2_mod_A_GLUD2)

performance::check_model(GluD2_mod_A_GLUD2, detrend = TRUE)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

GluD2_mod_A_GLUD2_dharma <- DHARMa::simulateResiduals(GluD2_mod_A_GLUD2, plot = F, n = nsim, seed = getOption("seed"))
GluD2_mod_A_GLUD2_dharma_t <- GluD2_mod_A_GLUD2_dharma$simulatedResponse |> t()
```

```{r fig.width = 10}
ppc_plots(GluD2_mod_A_GLUD2, simulations = GluD2_mod_A_GLUD2_dharma_t, term = "Condition")
ppc_plots(GluD2_mod_A_GLUD2, simulations = GluD2_mod_A_GLUD2_dharma_t, term = "Z")
```

```{r fig.width = 10}
ppc_stat_plots(GluD2_mod_A_GLUD2, simulations = GluD2_mod_A_GLUD2_dharma_t, term = "Condition")
ppc_stat_plots(GluD2_mod_A_GLUD2, simulations = GluD2_mod_A_GLUD2_dharma_t, term = "Z")
```

**Potential outliers:**

```{r fig.width = 10}
insight::get_data(GluD2_mod_A_GLUD2) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(GluD2_mod_A_GLUD2_dharma))
```


<!------------------------------------------------------------------------------>
## 4. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::parameters(
  GluD2_mod_A_GLUD2, exponentiate = should_exp(GluD2_mod_A_GLUD2), 
  ci_method = "Wald", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(GluD2_mod_A_GLUD2, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(GluD2_mod_A_GLUD2, pred = "Condition")
```


<!------------------------------------------------------------------------------>
### Marginal Effects:

**Condition:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(GluD2_mod_A_GLUD2), dvs = insight::find_response(GluD2_mod_A_GLUD2), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(GluD2_mod_A_GLUD2, specs = "Condition", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(GluD2_mod_A_GLUD2, specs = "Condition", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(GluD2_mod_A_GLUD2, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 4, fig.height = 7}
make_signif_boxplot(GluD2_mod_A_GLUD2, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(GluD2_mod_A_GLUD2)}] Boxplots - by [Condition]"), subfolder = GluD2_target, dpi = 600, width = 5, height = 8)
```

**Z:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(GluD2_mod_A_GLUD2), dvs = insight::find_response(GluD2_mod_A_GLUD2), between = "Z")

log.main("===[Emmeans]===\n")

emmeans::emmeans(GluD2_mod_A_GLUD2, specs = "Z", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(GluD2_mod_A_GLUD2, specs = "Z", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(GluD2_mod_A_GLUD2, specs = "Z", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 4, fig.height = 7}
make_signif_boxplot(GluD2_mod_A_GLUD2, xaxis = "Z") |> 
  save_png(filename = glue("[{get_model_tag(GluD2_mod_A_GLUD2)}] Boxplots - by [Z]"), subfolder = GluD2_target, dpi = 600, width = 4.5, height = 7)
```

**Condition:Z**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(GluD2_mod_A_GLUD2), dvs = insight::find_response(GluD2_mod_A_GLUD2), between = c("Condition", "Z"))

log.main("===[Emmeans]===\n")

emmeans::emmeans(GluD2_mod_A_GLUD2, specs = ~ Condition | Z, type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(GluD2_mod_A_GLUD2, specs = ~ Condition | Z, type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(GluD2_mod_A_GLUD2, specs = ~ Condition | Z, type = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(GluD2_mod_A_GLUD2, specs = ~ Condition | Z, trans = "response") |>
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(GluD2_mod_A_GLUD2, specs = ~ Condition | Z, trans = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)
```

Plots:

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot(GluD2_mod_A_GLUD2, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(GluD2_mod_A_GLUD2)}] Boxplots - by [Condition] within [Z]"), subfolder = GluD2_target, dpi = 600, width = 10, height = 7)
```

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot_inter(GluD2_mod_A_GLUD2, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(GluD2_mod_A_GLUD2)}] Interaction Boxplots - by [Condition] within [Z]"), subfolder = GluD2_target, dpi = 600, width = 10, height = 7)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# IV. Vol_GLUD2:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distributions:

**By Condition:**

```{r}
distribution_summary(GluD2_data, dvs = "Vol_GLUD2", between = "Condition")
```

```{r}
hist_plot(GluD2_data, var = "Vol_GLUD2", facet = "Condition")
```

**By Z:**

```{r}
distribution_summary(GluD2_data, dvs = "Vol_GLUD2", between = "Z")
```

```{r}
hist_plot(GluD2_data, var = "Vol_GLUD2", facet = "Z")
```

**By Condition:Z:**

```{r}
distribution_summary(GluD2_data, dvs = "Vol_GLUD2", between = c("Condition", "Z"))
```

```{r}
hist_plot(GluD2_data, var = "Vol_GLUD2") + facet_grid(rows = vars(Z), cols = vars(Condition))
```


<!------------------------------------------------------------------------------>
## 2. Models:
***

<!------------------------------------------------------------------------------>
### Welch t-test:

On data aggregated by Mouse.
Data is assumed heteroscedastic in relation to `Condition`.

```{r}
GluD2_mod_Vol_GLUD2_agg <- afex::mixed(
  Vol_GLUD2 ~ Condition + (0 + dCondition | ID),
  data = GluD2_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(GluD2_mod_Vol_GLUD2_agg$full_model, effects = "fixed", ci_method = "wald", drop = "Intercept")
```


<!------------------------------------------------------------------------------>
### GLMM:

**Gaussian:**

```{r}
GluD2_mod_Vol_GLUD2_gauss <- glmmTMB::glmmTMB(
  Vol_GLUD2 ~ Condition * Z + (1 | Mouse),
  family = gaussian("log"),
  data = GluD2_data,
  REML = T
)

parameters::parameters(GluD2_mod_Vol_GLUD2_gauss)
cat("\n\n")
performance::performance(GluD2_mod_Vol_GLUD2_gauss)
```

**Gamma:**

```{r}
GluD2_mod_Vol_GLUD2_gamma <- glmmTMB::glmmTMB(
  Vol_GLUD2 ~ Condition * Z + (1 | Mouse),
  family = Gamma("log"),
  data = GluD2_data,
  REML = T,
  control = glmmTMBControl(optimizer = optim, optArgs = list(method = "BFGS"))
)

parameters::parameters(GluD2_mod_Vol_GLUD2_gamma)
cat("\n\n")
performance::performance(GluD2_mod_Vol_GLUD2_gamma)
```

<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(GluD2_mod_Vol_GLUD2_gauss, GluD2_mod_Vol_GLUD2_gamma)
```

Best model:

```{r}
GluD2_mod_Vol_GLUD2 <- GluD2_mod_Vol_GLUD2_gamma
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 8}
make_acf_plot(GluD2_mod_Vol_GLUD2)

performance::check_model(GluD2_mod_Vol_GLUD2, detrend = TRUE)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

GluD2_mod_Vol_GLUD2_dharma <- DHARMa::simulateResiduals(GluD2_mod_Vol_GLUD2, plot = F, n = nsim, seed = getOption("seed"))
GluD2_mod_Vol_GLUD2_dharma_t <- GluD2_mod_Vol_GLUD2_dharma$simulatedResponse |> t()
```

```{r fig.width = 10}
ppc_plots(GluD2_mod_Vol_GLUD2, simulations = GluD2_mod_Vol_GLUD2_dharma_t, term = "Condition")
ppc_plots(GluD2_mod_Vol_GLUD2, simulations = GluD2_mod_Vol_GLUD2_dharma_t, term = "Z")
```

```{r fig.width = 10}
ppc_stat_plots(GluD2_mod_Vol_GLUD2, simulations = GluD2_mod_Vol_GLUD2_dharma_t, term = "Condition")
ppc_stat_plots(GluD2_mod_Vol_GLUD2, simulations = GluD2_mod_Vol_GLUD2_dharma_t, term = "Z")
```

**Potential outliers:**

```{r fig.width = 10}
insight::get_data(GluD2_mod_Vol_GLUD2) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(GluD2_mod_Vol_GLUD2_dharma))
```


<!------------------------------------------------------------------------------>
## 4. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::parameters(
  GluD2_mod_Vol_GLUD2, exponentiate = should_exp(GluD2_mod_Vol_GLUD2), 
  ci_method = "Wald", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(GluD2_mod_Vol_GLUD2, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(GluD2_mod_Vol_GLUD2, pred = "Condition")
```

<!------------------------------------------------------------------------------>
### Marginal Effects:

**Condition:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(GluD2_mod_Vol_GLUD2), dvs = insight::find_response(GluD2_mod_Vol_GLUD2), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(GluD2_mod_Vol_GLUD2, specs = "Condition", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(GluD2_mod_Vol_GLUD2, specs = "Condition", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(GluD2_mod_Vol_GLUD2, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 4, fig.height = 7}
make_signif_boxplot(GluD2_mod_Vol_GLUD2, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(GluD2_mod_Vol_GLUD2)}] Boxplots - by [Condition]"), subfolder = GluD2_target, dpi = 600, width = 5, height = 8)
```

**Z:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(GluD2_mod_Vol_GLUD2), dvs = insight::find_response(GluD2_mod_Vol_GLUD2), between = "Z")

log.main("===[Emmeans]===\n")

emmeans::emmeans(GluD2_mod_Vol_GLUD2, specs = "Z", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(GluD2_mod_Vol_GLUD2, specs = "Z", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(GluD2_mod_Vol_GLUD2, specs = "Z", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 4, fig.height = 7}
make_signif_boxplot(GluD2_mod_Vol_GLUD2, xaxis = "Z") |> 
  save_png(filename = glue("[{get_model_tag(GluD2_mod_Vol_GLUD2)}] Boxplots - by [Z]"), subfolder = GluD2_target, dpi = 600, width = 4.5, height = 7)
```

**Condition:Z**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(GluD2_mod_Vol_GLUD2), dvs = insight::find_response(GluD2_mod_Vol_GLUD2), between = c("Condition", "Z"))

log.main("===[Emmeans]===\n")

emmeans::emmeans(GluD2_mod_Vol_GLUD2, specs = ~ Condition | Z, type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(GluD2_mod_Vol_GLUD2, specs = ~ Condition | Z, type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(GluD2_mod_Vol_GLUD2, specs = ~ Condition | Z, type = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(GluD2_mod_Vol_GLUD2, specs = ~ Condition | Z, trans = "response") |>
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.note("===[Interaction]===\n")

emmeans::emmeans(GluD2_mod_Vol_GLUD2, specs = ~ Condition | Z, trans = "response") |>
  emmeans::contrast(interaction = c("pairwise"), by = NULL, adjust = "none", infer = TRUE)
```

Plots:

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot(GluD2_mod_Vol_GLUD2, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(GluD2_mod_Vol_GLUD2)}] Boxplots - by [Condition] within [Z]"), subfolder = GluD2_target, dpi = 600, width = 10, height = 7)
```

```{r fig.width = 6, fig.height = 5}
make_signif_boxplot_inter(GluD2_mod_Vol_GLUD2, xaxis = "Condition", facet = "Z") |> 
  save_png(filename = glue("[{get_model_tag(GluD2_mod_Vol_GLUD2)}] Interaction Boxplots - by [Condition] within [Z]"), subfolder = GluD2_target, dpi = 600, width = 10, height = 7)
```

