```{r include = F, echo = F}
source("../src/init.R", echo = F)
```

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# I. Data:
*** 

```{r data}

mbp_target <- "MBP"

(mbp_data <- load_mbp(config$data$mbp_path))

### Variables:

mbp_responses <- c("Length_Fil", "Area_Fil", "Vol_Fil", "Angle_Fil")

Length_Fil_name <- "Length of myelinated fibers *(10^(-4) μm)*"
Area_Fil_name <- "Area of myelinated fibers *(10^(-4) μm^(2))*"
Vol_Fil_name <- "Volume of myelinated fibers *(10^(-4) μm^(3))*"

contrasts(mbp_data$Condition) <- contr.treatment

### Averaged data:

mbp_data_agg <- mbp_data |> 
  group_by(Mouse, Condition) |> 
  summarize(across(matches(mbp_responses), .fns = \(.x) mean(.x, na.rm = T))) |> 
  ungroup() |> 
  mutate(dCondition = as.numeric(Condition == "IH")) |> 
  rowid_to_column("ID")
```

```{r}
mbp_data %>% filter_all(any_vars(is.na(.)))
```


<!------------------------------------------------------------------------------>
## Correlations:
***

```{r fig.width = 9}
corr_matrix_plot(mbp_data, vars = c("Condition", mbp_responses))
```

```{r fig.width = 10}
GGally::ggpairs(
  mbp_data, columns = c("Condition", mbp_responses), 
  mapping = aes(color = Condition), lower = list(continuous = "smooth")
)
```

<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# II. Length_Fil:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distributions:

```{r}
distribution_summary(mbp_data, dvs = "Length_Fil", between = "Condition")
```

```{r fig.width = 6}
hist_plot(mbp_data, var = "Length_Fil", facet = "Condition")
```


<!------------------------------------------------------------------------------>
## 2. Models:
***

<!------------------------------------------------------------------------------>
### Welch t-test:

On data aggregated by Mouse.
Data is assumed heteroscedastic in relation to `Condition`.

```{r}
mbp_mod_Length_Fil_agg <- afex::mixed(
  Length_Fil ~ Condition + (0 + dCondition | ID),
  data = mbp_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(mbp_mod_Length_Fil_agg$full_model, effects = "fixed", ci_method = "satterthwaite", drop = "Intercept")
```


<!------------------------------------------------------------------------------>
### GLMM:

**Gaussian:**

```{r}
mbp_mod_Length_Fil_gauss <- glmmTMB(
  Length_Fil ~ Condition + (1 | Mouse),
  family = gaussian("log"),
  data = mbp_data,
  REML = T
)

parameters::parameters(mbp_mod_Length_Fil_gauss)
cat("\n\n")
performance::performance(mbp_mod_Length_Fil_gauss)
```

**Gamma:**

```{r}
mbp_mod_Length_Fil_gamma <- glmmTMB(
  Length_Fil ~ Condition + (1 | Mouse),
  family = Gamma("log"),
  data = mbp_data,
  REML = T
)

parameters::parameters(mbp_mod_Length_Fil_gamma)
cat("\n\n")
performance::performance(mbp_mod_Length_Fil_gamma)
```


<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(mbp_mod_Length_Fil_gauss, mbp_mod_Length_Fil_gamma)
```

Best model:

```{r}
mbp_mod_Length_Fil <- mbp_mod_Length_Fil_gamma
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 8}
make_acf_plot(mbp_mod_Length_Fil)

performance::check_model(mbp_mod_Length_Fil, detrend = TRUE)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

mbp_mod_Length_Fil_dharma <- DHARMa::simulateResiduals(mbp_mod_Length_Fil, plot = F, n = nsim, seed = getOption("seed"))
mbp_mod_Length_Fil_dharma_t <- mbp_mod_Length_Fil_dharma$simulatedResponse |> t()
```

```{r fig.width = 8}
ppc_plots(mbp_mod_Length_Fil, mbp_mod_Length_Fil_dharma_t, term = "Condition")
```

```{r fig.width = 8}
ppc_stat_plots(mbp_mod_Length_Fil, mbp_mod_Length_Fil_dharma_t, term = "Condition")
```

**Potential outliers:**

```{r}
insight::get_data(mbp_mod_Length_Fil) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(mbp_mod_Length_Fil_dharma))
```


<!------------------------------------------------------------------------------>
## 4. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::model_parameters(
  mbp_mod_Length_Fil, exponentiate = should_exp(mbp_mod_Length_Fil), 
  ci_method = "Kenward", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(mbp_mod_Length_Fil, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(mbp_mod_Length_Fil, pred = "Condition")
```


<!------------------------------------------------------------------------------>
### Marginal Effects:

**Condition:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(mbp_mod_Length_Fil), dvs = insight::find_response(mbp_mod_Length_Fil), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(mbp_mod_Length_Fil, specs = "Condition", type = "response")
```

Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(mbp_mod_Length_Fil, specs = "Condition", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(mbp_mod_Length_Fil, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 2, fig.height = 3}
make_signif_boxplot(mbp_mod_Length_Fil, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(mbp_mod_Length_Fil)}] Boxplot - by [Condition]"), subfolder = mbp_target, dpi = 600, width = 5, height = 8)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# III. Area_Fil:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distributions:

```{r}
distribution_summary(mbp_data, dvs = "Area_Fil", between = "Condition")
```

```{r fig.width = 6}
hist_plot(mbp_data, var = "Area_Fil", facet = "Condition")
```


<!------------------------------------------------------------------------------>
## 2. Models:
***

<!------------------------------------------------------------------------------>
### Welch t-test:

On data aggregated by Mouse.
Data is assumed heteroscedastic in relation to `Condition`.

```{r}
mbp_mod_Area_Fil_agg <- afex::mixed(
  Area_Fil ~ Condition + (0 + dCondition | ID),
  data = mbp_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(mbp_mod_Area_Fil_agg$full_model, effects = "fixed", ci_method = "satterthwaite", drop = "Intercept")
```


<!------------------------------------------------------------------------------>
### GLMM:

**Gaussian:**

```{r}
mbp_mod_Area_Fil_gauss <- glmmTMB(
  Area_Fil ~ Condition + (1 | Mouse),
  family = gaussian("log"),
  data = mbp_data,
  REML = T
)

parameters::parameters(mbp_mod_Area_Fil_gauss)
cat("\n\n")
performance::performance(mbp_mod_Area_Fil_gauss)
```

**Gamma:**

```{r}
mbp_mod_Area_Fil_gamma <- glmmTMB(
  Area_Fil ~ Condition + (1 | Mouse),
  family = Gamma("log"),
  data = mbp_data,
  REML = T
)

parameters::parameters(mbp_mod_Area_Fil_gamma)
cat("\n\n")
performance::performance(mbp_mod_Area_Fil_gamma)
```


<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(mbp_mod_Area_Fil_gauss, mbp_mod_Area_Fil_gamma)
```

Best model:

```{r}
mbp_mod_Area_Fil <- mbp_mod_Area_Fil_gamma
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 10}
make_acf_plot(mbp_mod_Area_Fil)

performance::check_model(mbp_mod_Area_Fil, detrend = TRUE)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

mbp_mod_Area_Fil_dharma <- DHARMa::simulateResiduals(mbp_mod_Area_Fil, plot = F, n = nsim, seed = getOption("seed"))
mbp_mod_Area_Fil_dharma_t <- mbp_mod_Area_Fil_dharma$simulatedResponse |> t()
```

```{r fig.width = 8}
ppc_plots(mbp_mod_Area_Fil, mbp_mod_Area_Fil_dharma_t, term = "Condition")
```

```{r fig.width = 8}
ppc_stat_plots(mbp_mod_Area_Fil, mbp_mod_Area_Fil_dharma_t, term = "Condition")
```

**Potential outliers:**

```{r}
insight::get_data(mbp_mod_Area_Fil) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(mbp_mod_Area_Fil_dharma))
```


<!------------------------------------------------------------------------------>
## 4. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::model_parameters(
  mbp_mod_Area_Fil, exponentiate = should_exp(mbp_mod_Area_Fil), 
  ci_method = "Kenward", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(mbp_mod_Area_Fil, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(mbp_mod_Area_Fil, pred = "Condition")
```


<!------------------------------------------------------------------------------>
### Marginal Effects:

**Condition:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(mbp_mod_Area_Fil), dvs = insight::find_response(mbp_mod_Area_Fil), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(mbp_mod_Area_Fil, specs = "Condition", type = "response")
```

Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(mbp_mod_Length_Fil, specs = "Condition", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(mbp_mod_Length_Fil, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 2, fig.height = 3}
make_signif_boxplot(mbp_mod_Area_Fil, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(mbp_mod_Area_Fil)}] Boxplot - by [Condition]"), subfolder = mbp_target, dpi = 600, width = 5, height = 8)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
# IV. Vol_Fil:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:
***

<!------------------------------------------------------------------------------>
### Distributions:

```{r}
distribution_summary(mbp_data, dvs = "Vol_Fil", between = "Condition")
```

```{r fig.width = 6}
hist_plot(mbp_data, var = "Vol_Fil", facet = "Condition")
```


<!------------------------------------------------------------------------------>
## 2. Models:
***

<!------------------------------------------------------------------------------>
### a. Welch t-test:

On data aggregated by Mouse.
Data is assumed heteroscedastic in relation to `Condition`.

```{r}
mbp_mod_Vol_Fil_agg <- afex::mixed(
  Vol_Fil ~ Condition + (0 + dCondition | ID),
  data = mbp_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(mbp_mod_Vol_Fil_agg$full_model, effects = "fixed", ci_method = "satterthwaite", drop = "Intercept")
```


<!------------------------------------------------------------------------------>
### b. GLMM:

**Gaussian:**

```{r}
mbp_mod_Vol_Fil_gauss <- glmmTMB(
  Vol_Fil ~ Condition + (1 | Mouse),
  family = gaussian("log"),
  data = mbp_data,
  REML = T
)

parameters::parameters(mbp_mod_Vol_Fil_gauss)
cat("\n\n")
performance::performance(mbp_mod_Vol_Fil_gauss)
```

**Gamma:**

```{r}
mbp_mod_Vol_Fil_gamma <- glmmTMB(
  Vol_Fil ~ Condition + (1 | Mouse),
  family = Gamma("log"),
  data = mbp_data,
  REML = T
)

parameters::parameters(mbp_mod_Vol_Fil_gamma)
cat("\n\n")
performance::performance(mbp_mod_Vol_Fil_gamma)
```


<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:
***

**Model comparison:**

```{r}
performance::compare_performance(mbp_mod_Vol_Fil_gauss, mbp_mod_Vol_Fil_gamma)
```

Best model:

```{r}
mbp_mod_Vol_Fil <- mbp_mod_Vol_Fil_gamma
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 8}
make_acf_plot(mbp_mod_Vol_Fil)

performance::check_model(mbp_mod_Vol_Fil, detrend = TRUE)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

mbp_mod_Vol_Fil_dharma <- DHARMa::simulateResiduals(mbp_mod_Vol_Fil, plot = F, n = nsim, seed = getOption("seed"))
mbp_mod_Vol_Fil_dharma_t <- mbp_mod_Vol_Fil_dharma$simulatedResponse |> t()
```

```{r fig.width = 8}
ppc_plots(mbp_mod_Vol_Fil, mbp_mod_Vol_Fil_dharma_t, term = "Condition")
```

```{r fig.width = 8}
ppc_stat_plots(mbp_mod_Vol_Fil, mbp_mod_Vol_Fil_dharma_t, term = "Condition")
```

**Potential outliers:**

```{r}
insight::get_data(mbp_mod_Vol_Fil) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(mbp_mod_Vol_Fil_dharma))
```


<!------------------------------------------------------------------------------>
## 4. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::model_parameters(
  mbp_mod_Vol_Fil, exponentiate = should_exp(mbp_mod_Vol_Fil), 
  ci_method = "Kenward", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(mbp_mod_Vol_Fil, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(mbp_mod_Vol_Fil, pred = "Condition")
```


<!------------------------------------------------------------------------------>
### Marginal Effects:

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(mbp_mod_Vol_Fil), dvs = insight::find_response(mbp_mod_Vol_Fil), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(mbp_mod_Vol_Fil, specs = "Condition", type = "response")
```

Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(mbp_mod_Vol_Fil, specs = "Condition", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(mbp_mod_Vol_Fil, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 2, fig.height = 3}
make_signif_boxplot(mbp_mod_Vol_Fil, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(mbp_mod_Vol_Fil)}] Boxplot - by [Condition]"), subfolder = mbp_target, dpi = 600, width = 5, height = 8)
```

