```{r include = F, echo = F}
source("../src/setup.R", echo = F)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# I. Data:
***

```{r data}

ROS_target <- "ROS"

(ROS_data <- load_ROS(config$data$ROS_path))

### Variables:

ROS_responses <- c("ROS_perc")
ROS_predictors <- c("Condition", "Mouse")

ROS_perc_name <- "ROS  \n *(% of control)*"

contrasts(ROS_data$Condition) <- contr.treatment
```

```{r}
ROS_data %>% filter_all(any_vars(is.na(.)))
```

<!------------------------------------------------------------------------------>
## Correlations:
***

```{r fig.width = 8}
corr_matrix_plot(ROS_data, vars = c(ROS_predictors, ROS_responses))
```

```{r fig.width = 8}
GGally::ggpairs(
  ROS_data, columns = c("Condition", ROS_responses), 
  mapping = aes(color = Condition), lower = list(continuous = "smooth")
)
```


<!------------------------------------------------------------------------------>
<!------------------------------------------------------------------------------>
***
# II. ROS_perc:
***

<!------------------------------------------------------------------------------>
## 1. Data Exploration:

```{r}
distribution_summary(ROS_data, dvs = "ROS_perc", between = "Condition")
```

```{r fig.width = 6}
hist_plot(ROS_data, var = "ROS_perc")
```


<!------------------------------------------------------------------------------>
## 2. Models:
***

<!------------------------------------------------------------------------------>
### Welch t-test:

Data is already aggregate per Mouse.

```{r}
(ROS_data_agg <- ROS_data |> 
  mutate(dCondition = as.numeric(Condition == "IH")) |> 
  rowid_to_column("ID")
)
```

Welch t-test:

```{r}
ROS_mod_perc_agg <- afex::mixed(
  ROS_perc ~ Condition + (0 + dCondition | ID),
  data = ROS_data_agg,
  control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.nRE = "ignore"),
  check_contrasts = F,
  method = "S",
  type = 3,
  test_intercept = FALSE
)

parameters(ROS_mod_perc_agg$full_model, effects = "fixed", ci_method = "satterthwaite", drop = "Intercept")
```

Mann-Whitney:

```{r}
wilcox.test(formula = ROS_perc ~ Condition, data = ROS_data_agg)
```

<!------------------------------------------------------------------------------>
### GLM:

**Gaussian:**

```{r}
ROS_mod_perc_gauss <- glmmTMB(
  ROS_perc ~ Condition,
  family = gaussian("log"),
  data = ROS_data,
  REML = T
)

parameters::parameters(ROS_mod_perc_gauss)
cat("\n")
performance::performance(ROS_mod_perc_gauss)
```

**Gamma:**

```{r}
ROS_mod_perc_gamma <- glmmTMB(
  ROS_perc ~ Condition,
  family = Gamma("log"),
  data = ROS_data,
  REML = T
)

parameters::parameters(ROS_mod_perc_gamma)
cat("\n")
performance::performance(ROS_mod_perc_gamma)
```


<!------------------------------------------------------------------------------>
## 3. Model Diagnostics:

**Model comparison:**

```{r}
performance::compare_performance(ROS_mod_perc_gauss, ROS_mod_perc_gamma)
```

Best model:

```{r}
ROS_mod_perc <- ROS_mod_perc_gamma
```


<!------------------------------------------------------------------------------>
### Residuals:

```{r fig.width = 8}
make_acf_plot(ROS_mod_perc)

performance::check_model(ROS_mod_perc, detrend = TRUE)
```


<!------------------------------------------------------------------------------>
### Predictions:

```{r}
nsim <- 300

ROS_mod_perc_dharma <- DHARMa::simulateResiduals(ROS_mod_perc, plot = F, n = nsim, seed = getOption("seed"))
ROS_mod_perc_dharma_t <- ROS_mod_perc_dharma$simulatedResponse |> t()
```

```{r fig.width = 10}
ppc_plots(ROS_mod_perc, ROS_mod_perc_dharma_t, term = "Condition")
```

```{r fig.width = 10}
ppc_stat_plots(ROS_mod_perc, ROS_mod_perc_dharma_t, term = "Condition")
```

**Potential outliers:**

```{r}
insight::get_data(ROS_mod_perc) |> 
  rownames_to_column("ID") |> 
  filter(ID %in% DHARMa::outliers(ROS_mod_perc_dharma))
```


<!------------------------------------------------------------------------------>
## 4. Effects Analysis:
***

<!------------------------------------------------------------------------------>
### Coefficients:

**All effects (Wald):**

```{r}
parameters::parameters(
  ROS_mod_perc, exponentiate = should_exp(ROS_mod_perc), 
  ci_method = "Kenward", p_adjust = "none", summary = T, digits = 3
)
```

**Main effects (Wald):**

```{r}
car::Anova(ROS_mod_perc, type = 3)
```

**Main effects (LRT):**

```{r}
LRT(ROS_mod_perc, pred = "Condition")
```


<!------------------------------------------------------------------------------>
### Marginal Effects:

**Condition:**

Marginal Means:

```{r}
log.main("===[Observed]===\n")

distribution_summary(insight::get_data(ROS_mod_perc), dvs = insight::find_response(ROS_mod_perc), between = "Condition")

log.main("===[Emmeans]===\n")

emmeans::emmeans(ROS_mod_perc, specs = "Condition", type = "response")
```

Marginal Contrasts:

```{r}
log.main("===[Link scale]===\n")

emmeans::emmeans(ROS_mod_perc, specs = "Condition", type = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)

log.main("===[Response scale]===\n")

emmeans::emmeans(ROS_mod_perc, specs = "Condition", trans = "response") |> 
  emmeans::contrast(method = "pairwise", adjust = "none", infer = TRUE)
```

Plot:

```{r fig.width = 5, fig.height = 8}
make_signif_boxplot(ROS_mod_perc, xaxis = "Condition") |> 
  save_png(filename = glue("[{get_model_tag(ROS_mod_perc)}] Boxplots - by [Condition]"), subfolder = ROS_target, dpi = dpi_save_png, width = 5, height = 8)
```